### 2023-04-22 Article.Rmd
1

---
title             : "From Likes to Change: Assessing the Impact of Citizen Engagement on the European Commission's Social Media Platforms"
shorttitle        : "From Likes to Change: Assessing the Impact of Citizen Engagement on the European Commission's Social Media Platforms"

author: 
  - name          : "Tanase Tasențe"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "tanase.tasente@365.univ-ovidius.ro"
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - "Conceptualization"
      - "Writing - Original Draft Preparation"
      - "Writing - Review & Editing"
  - name          : "Cristian Opariuc-Dan"
    affiliation   : "1"
    role:
      - "Writing - Review & Editing"
      - "Supervision"

affiliation:
  - id            : "1"
    institution   : "Faculty of Law and Administrative Sciences, Ovidius University of Constanta, Romania"

authornote: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

  Enter author note here.

abstract: |
  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.

  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.

  One sentence clearly stating the **general problem** being addressed by  this particular study.

  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).

  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.

  One or two sentences to put the results into a more **general context**.

  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.

  <!-- https://tinyurl.com/ybremelq -->

keywords          : "keywords"
wordcount         : "X"

bibliography      : "references.bib"

floatsintext      : no
linenumbers       : yes
draft             : no
mask              : no

figurelist        : no
tablelist         : no
footnotelist      : no

classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
library("papaja")
r_refs("references.bib")
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```
# Introduction
In recent years, the rise of social media platforms has led to significant changes in the way institutions, including public organizations, communicate with their audiences. As a result, the importance of citizen engagement in the process of communication through social media has become increasingly recognized. This engagement involves not only a one-way flow of information from public institutions to citizens, but also an interactive dialogue between the two parties.
The concept of engagement in social media has been studied extensively in recent years, with researchers exploring various aspects of this phenomenon. One such study, conducted by @dolanSocialMediaEngagement2016 approached social media engagement behavior from a uses and gratifications perspective, focusing on the motivations and benefits that users derive from engaging with social media. Meanwhile, the study by @dragsethBuildingStudentEngagement2020 explored how social media can be used to build engagement among students in the context of political science education.
Another important aspect of engagement in social media is the role it plays in activation campaigns aimed at consumers. @mirbagheriConsumersEngagementSocial2019 conceptualized and developed a scale to measure consumers' engagement with social media activation campaigns. Additionally, @smithTermsEngagementAnalyzing2015a analyzed public engagement with organizations through social media, highlighting the importance of two-way communication between public institutions and citizens.
The differentiating role of platform type in engagement with social media and social media advertising was explored by @voorveldEngagementSocialMedia2018, who found that the level of engagement varies across different social media platforms.
In addition to understanding the various aspects of engagement in social media, it is also important to recognize the significance of citizen engagement in the context of public institutions. Citizen engagement plays a critical role in ensuring transparency and accountability in public decision-making processes. Furthermore, engagement with citizens can lead to the development of more effective policies and programs that better serve the needs of the community.
Moreover, the importance of citizen engagement in the process of communication through social media cannot be overstated. Through social media, public institutions can engage in an interactive dialogue with citizens, build trust, and develop more effective policies and programs. As such, further research, and exploration of the concept of engagement in social media is critical for ensuring that public institutions continue to effectively communicate with and serve the needs of their communities.
Citizen engagement through social media can also contribute to the empowerment of individuals and groups, giving them a voice in public decision-making processes and enabling them to hold public institutions accountable for their actions. This can help to build stronger, more resilient communities that are better equipped to respond to challenges and opportunities.
It is also important to note that while social media has the potential to be a powerful tool for citizen engagement, there are also challenges and risks associated with its use. These include issues related to privacy, security, and the spread of misinformation and disinformation. As such, public institutions must be mindful of these risks and take steps to mitigate them, while also leveraging the power of social media to engage with citizens in a meaningful way.
Overall, the rise of social media has transformed the way public institutions communicate with citizens, placing a greater emphasis on engagement and two-way communication. Understanding the various aspects of engagement in social media is critical for public institutions to effectively communicate with and serve the needs of their communities. By leveraging the power of social media to engage with citizens, public institutions can build trust, empower individuals and groups, and develop more effective policies and programs that better serve the needs of the community.

# Literature review
In the past few years, social media has risen to become a significant means of communication between public institutions and citizens. This has paved the way for increased citizen engagement in the decision-making process, which is considered essential for fostering trust and enhancing accountability. This literature review delves into the significance of citizen involvement in the communication process of public institutions via social media. It does so by amalgamating and synthesizing the findings of diverse studies, each focusing on various facets of social media and citizen engagement within the European Union. 
@beneKeepThemEngaged2022 conducted a study exploring the impacts of self-centered social media communication styles on user engagement across 12 European nations. Their findings revealed that social media communication emphasizing user participation and fostering feedback effectively boosts user engagement. Social media users who feel they have a say in the decision-making process are more inclined to engage and participate in conversations. @dewildeAnalyzingCitizenEngagement2022 examined citizen engagement with European politics on social media platforms and discovered that social media holds the potential to increase citizen involvement and participation in the political sphere. They found that social media offers citizens a platform to express their opinions, partake in discussions, and influence policy-making decisions. In a similar vein, @bankstonMigrationSmugglingVirtual2021 investigated the role of social media in migration and smuggling across the European Union's virtual borders. This study concluded that social media platforms offer citizens opportunities to engage in dialogues and share their perspectives on immigration policies.
@cinelliPromotingEngagementQuality2022, on the other hand, delved into promoting engagement with quality communication in social media. Their findings indicated that employing persuasive language, evoking emotions, and utilizing framing can enhance user engagement. The study recommends that public institutions implement quality communication techniques to boost citizen engagement and participation in policy-making. @mullerSpreadingWordEuropean2022 analyzed the social media attention garnered by European Union agencies and found a positive correlation between increased attention and higher levels of citizen engagement. This study implies that public institutions can augment citizen engagement by effectively utilizing social media to showcase their activities and interact with citizens.
Additionally, @rusSocialMediaCommunication2021 carried out a case study investigating the representation of the European Commission in Romania via social media communication. The study established that social media communication by public institutions can bolster transparency and accountability, consequently leading to heightened citizen engagement. @hancu-buduiAuditInstitutionsEuropean2020 examined the communication strategies employed by audit institutions in the European Union during the Covid-19 crisis. Their findings suggested that social media can serve as a potent tool for promoting public services and encouraging environmental engagement. The study advocates for public institutions to harness social media to showcase their activities and connect with citizens during times of crisis. @kanolGroupTypeSocial2021a scrutinized the social media engagement tactics of British interest groups on Facebook. They found that group type influences social media engagement strategies, with non-profit groups being more inclined to utilize user-generated content and participatory approaches. The study implies that public institutions can adopt lessons from non-profit groups and employ participatory strategies to elevate citizen engagement.
Finally, @weiExploringPublicOpinions2021 executed a case study analyzing public opinions on climate change policy in the European Union using Twitter data. The study concluded that social media offers a platform for citizens to discuss climate change policies, suggesting that public institutions should leverage social media to engage with citizens on critical issues like climate change.

# Case study
## Research objectives
The overall objective of this research is to analyze and compare the online engagement of the public on various official social media platforms (Facebook, Instagram, Twitter, and YouTube) of the European Commission.

## Research tool
The research instrument used in this study involved the extraction and analysis of data from the official Facebook, Twitter, Instagram, and Youtube pages of the European Commission. To collect this data, the Fanpagekarma  platform was used, which is a popular tool for social media analytics and monitoring.
The data extracted from the platform included the post ID, message content, post type, post date, number of likes, comments, shares, and rounded number of followers for each post made by the European Commission between 24 March 2023 and 20 April 2023. 
To calculate the engagement rate, the total number of reactions (likes, comments, and shares) was divided by the number of followers. This metric is often used to measure the level of audience interaction with a brand or organization on social media.

## Overview of data analysis
The data collected from this research instrument was analyzed using various statistical techniques, including descriptive statistics and ……. Descriptive statistics were used to summarize the data and identify trends and patterns in the engagement rates, likes, comments, and shares for each post type and platform. 
In this analysis, we will examine the social media performance of the European Commission's Facebook, Instagram, Twitter, and Youtube accounts during the period from 24 March 2023 to 20 April 2023. We will focus on the engagement rate (ER) of each platform, which measures the percentage of followers who engage with a post by liking, commenting, sharing, or otherwise interacting with it.

## Data analysis
We used `r cite_r("references.bib")` for all our analyses.

# Results

# Discussion

\newpage

# References

::: {#refs custom-style="Bibliography"}
:::

### 2023-04-22 analiza.R

@@ -10,7 +10,7 @@ youtube <- read_xlsx("youtube.xlsx"); youtube$Page <- "Youtube"; youtube$ER = yo
 date <- rbind(facebook,twitter, youtube,instagram); date$ER = date$Reactions/date$Fans
 
 #Salvare set de date####
-write_xlsx(x = date, path = "fbbucha.xlsx", col_names = TRUE)
+write_xlsx(x = date, path = "date.xlsx", col_names = TRUE)
 
 #Nr. postari / canal####
 date %>%

### 2023-04-22 Article.Rmd
Articol cu introducerea

@@
 title             : "From Likes to Change: Assessing the Impact of Citizen Engagement on the European Commission's Social Media Platforms"
-shorttitle        : "From Likes to Change: Assessing the Impact of Citizen Engagement on the European Commission's Social Media Platforms"
+shorttitle        : "Impact of Citizen Engagement on the European Commission's Social Media Platforms"
 
 author: 
-  - name          : "Tanase Tasențe"
+  - name          : "Tănase Tasențe"
     affiliation   : "1"
@@
     address       : "Postal address"
-    email         : "tanase.tasente@365.univ-ovidius.ro"
+    email         : "my@email.com"
     role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
@@
   - name          : "Cristian Opariuc-Dan"
-    affiliation   : "1"
+    affiliation   : "1,2"
     role:
@@
   - id            : "1"
-    institution   : "Faculty of Law and Administrative Sciences, Ovidius University of Constanta, Romania"
+    institution   : "Ovidius University, Constanța"
+  - id            : "2"
+    institution   : "Bucharest University"
 
@@
 wordcount         : "X"
-
-bibliography      : "references.bib"
-
+bibliography      : ["r-references.bib", "Convergenta.bib"]
 floatsintext      : no
@@
 mask              : no
-
 figurelist        : no
@@
 footnotelist      : no
-
+documentclass     : "apa7"
 classoption       : "man"
-output            : papaja::apa6_pdf
+csl               : apa.csl
+output            :
+  pdf_document    : papaja::apa6_pdf
+  word_document   : papaja::apa6_docx
+header-includes:
+  - \usepackage{ragged2e}
 ---
@@
 ```{r setup, include = FALSE}
-library("papaja")
-r_refs("references.bib")
+  library(papaja)
+  r_refs("r-references.bib")
 ```
@@
 # Seed for random number generation
-set.seed(42)
+  set.seed(44542)
   knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
@@
 # Introduction
+\justify
 In recent years, the rise of social media platforms has led to significant changes in the way institutions, including public organizations, communicate with their audiences.
@@
 This engagement involves not only a one-way flow of information from public institutions to citizens, but also an interactive dialogue between the two parties.
+
 The concept of engagement in social media has been studied extensively in recent years, with researchers exploring various aspects of this phenomenon.
-One such study, conducted by @dolanSocialMediaEngagement2016 approached social media engagement behavior from a uses and gratifications perspective, focusing on the motivations and benefits that users derive from engaging with social media.
-Meanwhile, the study by @dragsethBuildingStudentEngagement2020 explored how social media can be used to build engagement among students in the context of political science education.
+One such study, conducted by @Dolan2016, approached social media engagement behavior from a uses and gratifications perspective, focusing on the motivations and benefits that users derive from engaging with social media.
+Meanwhile, the study by @Dragseth2020 explored how social media can be used to build engagement among students in the context of political science education.
+
 Another important aspect of engagement in social media is the role it plays in activation campaigns aimed at consumers.
-@mirbagheriConsumersEngagementSocial2019 conceptualized and developed a scale to measure consumers' engagement with social media activation campaigns.
-Additionally, @smithTermsEngagementAnalyzing2015a analyzed public engagement with organizations through social media, highlighting the importance of two-way communication between public institutions and citizens.
-The differentiating role of platform type in engagement with social media and social media advertising was explored by @voorveldEngagementSocialMedia2018, who found that the level of engagement varies across different social media platforms.
+@Mirbagheri2019 conceptualized and developed a scale to measure consumers' engagement with social media activation campaigns.
+Additionally, @Smith2015 analyzed public engagement with organizations through social media, highlighting the importance of two-way communication between public institutions and citizens.
+
+The differentiating role of platform type in engagement with social media and social media advertising was explored by @Voorveld2018, who found that the level of engagement varies across different social media platforms.
+
 In addition to understanding the various aspects of engagement in social media, it is also important to recognize the significance of citizen engagement in the context of public institutions.
@@
 Furthermore, engagement with citizens can lead to the development of more effective policies and programs that better serve the needs of the community.
+
 Moreover, the importance of citizen engagement in the process of communication through social media cannot be overstated.
@@
 As such, further research, and exploration of the concept of engagement in social media is critical for ensuring that public institutions continue to effectively communicate with and serve the needs of their communities.
+
 Citizen engagement through social media can also contribute to the empowerment of individuals and groups, giving them a voice in public decision-making processes and enabling them to hold public institutions accountable for their actions.
 This can help to build stronger, more resilient communities that are better equipped to respond to challenges and opportunities.
+
 It is also important to note that while social media has the potential to be a powerful tool for citizen engagement, there are also challenges and risks associated with its use.
@@
 As such, public institutions must be mindful of these risks and take steps to mitigate them, while also leveraging the power of social media to engage with citizens in a meaningful way.
+
 Overall, the rise of social media has transformed the way public institutions communicate with citizens, placing a greater emphasis on engagement and two-way communication.
@@
 
-# Literature review
+##Literature review
 In the past few years, social media has risen to become a significant means of communication between public institutions and citizens.
@@
 It does so by amalgamating and synthesizing the findings of diverse studies, each focusing on various facets of social media and citizen engagement within the European Union.
-@beneKeepThemEngaged2022 conducted a study exploring the impacts of self-centered social media communication styles on user engagement across 12 European nations.
+
+@Bene2022 conducted a study exploring the impacts of self-centered social media communication styles on user engagement across 12 European nations.
 Their findings revealed that social media communication emphasizing user participation and fostering feedback effectively boosts user engagement.
 Social media users who feel they have a say in the decision-making process are more inclined to engage and participate in conversations.
-@dewildeAnalyzingCitizenEngagement2022 examined citizen engagement with European politics on social media platforms and discovered that social media holds the potential to increase citizen involvement and participation in the political sphere.
+@DeWilde2022 examined citizen engagement with European politics on social media platforms and discovered that social media holds the potential to increase citizen involvement and participation in the political sphere.
 They found that social media offers citizens a platform to express their opinions, partake in discussions, and influence policy-making decisions.
-In a similar vein, @bankstonMigrationSmugglingVirtual2021 investigated the role of social media in migration and smuggling across the European Union's virtual borders.
+In a similar vein, @Bankston2021 investigated the role of social media in migration and smuggling across the European Union's virtual borders.
 This study concluded that social media platforms offer citizens opportunities to engage in dialogues and share their perspectives on immigration policies.
-@cinelliPromotingEngagementQuality2022, on the other hand, delved into promoting engagement with quality communication in social media.
+
+@Cinelli2022, on the other hand, delved into promoting engagement with quality communication in social media.
 Their findings indicated that employing persuasive language, evoking emotions, and utilizing framing can enhance user engagement.
 The study recommends that public institutions implement quality communication techniques to boost citizen engagement and participation in policy-making.
-@mullerSpreadingWordEuropean2022 analyzed the social media attention garnered by European Union agencies and found a positive correlation between increased attention and higher levels of citizen engagement.
+@Muller2022 analyzed the social media attention garnered by European Union agencies and found a positive correlation between increased attention and higher levels of citizen engagement.
 This study implies that public institutions can augment citizen engagement by effectively utilizing social media to showcase their activities and interact with citizens.
-Additionally, @rusSocialMediaCommunication2021 carried out a case study investigating the representation of the European Commission in Romania via social media communication.
+
+Additionally, @Rus2021 carried out a case study investigating the representation of the European Commission in Romania via social media communication.
 The study established that social media communication by public institutions can bolster transparency and accountability, consequently leading to heightened citizen engagement.
-@hancu-buduiAuditInstitutionsEuropean2020 examined the communication strategies employed by audit institutions in the European Union during the Covid-19 crisis.
+@Hancu2020 examined the communication strategies employed by audit institutions in the European Union during the Covid-19 crisis.
 Their findings suggested that social media can serve as a potent tool for promoting public services and encouraging environmental engagement.
 The study advocates for public institutions to harness social media to showcase their activities and connect with citizens during times of crisis.
-@kanolGroupTypeSocial2021a scrutinized the social media engagement tactics of British interest groups on Facebook.
+@Kanol2021 scrutinized the social media engagement tactics of British interest groups on Facebook.
 They found that group type influences social media engagement strategies, with non-profit groups being more inclined to utilize user-generated content and participatory approaches.
 The study implies that public institutions can adopt lessons from non-profit groups and employ participatory strategies to elevate citizen engagement.
-Finally, @weiExploringPublicOpinions2021 executed a case study analyzing public opinions on climate change policy in the European Union using Twitter data.
+
+Finally, @Wei2021 executed a case study analyzing public opinions on climate change policy in the European Union using Twitter data.
 The study concluded that social media offers a platform for citizens to discuss climate change policies, suggesting that public institutions should leverage social media to engage with citizens on critical issues like climate change.
 
-# Case study
-## Research objectives
-The overall objective of this research is to analyze and compare the online engagement of the public on various official social media platforms (Facebook, Instagram, Twitter, and YouTube) of the European Commission.
+# Methods
+We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study.
+<!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->
 
-## Research tool
-The research instrument used in this study involved the extraction and analysis of data from the official Facebook, Twitter, Instagram, and Youtube pages of the European Commission.
-To collect this data, the Fanpagekarma  platform was used, which is a popular tool for social media analytics and monitoring.
-The data extracted from the platform included the post ID, message content, post type, post date, number of likes, comments, shares, and rounded number of followers for each post made by the European Commission between 24 March 2023 and 20 April 2023.
-To calculate the engagement rate, the total number of reactions (likes, comments, and shares) was divided by the number of followers.
-This metric is often used to measure the level of audience interaction with a brand or organization on social media.
+## Participants
 
-## Overview of data analysis
-The data collected from this research instrument was analyzed using various statistical techniques, including descriptive statistics and …….
-Descriptive statistics were used to summarize the data and identify trends and patterns in the engagement rates, likes, comments, and shares for each post type and platform.
-In this analysis, we will examine the social media performance of the European Commission's Facebook, Instagram, Twitter, and Youtube accounts during the period from 24 March 2023 to 20 April 2023.
-We will focus on the engagement rate (ER) of each platform, which measures the percentage of followers who engage with a post by liking, commenting, sharing, or otherwise interacting with it.
+## Material
+
+## Procedure
 
 ## Data analysis
-We used `r cite_r("references.bib")` for all our analyses.
+We used `r cite_r("r-references.bib")` for all our analyses.
 

### 2023-04-22 Article.Rmd

@@
 author: 
-  - name          : "Tănase Tasențe"
+  - name          : "Tanase Tasențe"
     affiliation   : "1"
@@
     address       : "Postal address"
-    email         : "my@email.com"
+    email         : "tanase.tasente@365.univ-ovidius.ro"
     role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
@@
 wordcount         : "X"
-bibliography      : ["r-references.bib", "Convergenta.bib"]
+bibliography      : ["r-references.bib", "references.bib"]
 floatsintext      : no
@@
 
-# Methods
-We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study.
-<!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->
+# Case study
+## Research objectives
+The overall objective of this research is to analyze and compare the online engagement of the public on various official social media platforms (Facebook, Instagram, Twitter, and YouTube) of the European Commission.
 
-## Participants
+## Research tool
+The research instrument used in this study involved the extraction and analysis of data from the official Facebook, Twitter, Instagram, and Youtube pages of the European Commission.
+To collect this data, the Fanpagekarma  platform was used, which is a popular tool for social media analytics and monitoring.
+The data extracted from the platform included the post ID, message content, post type, post date, number of likes, comments, shares, and rounded number of followers for each post made by the European Commission between 24 March 2023 and 20 April 2023.
+To calculate the engagement rate, the total number of reactions (likes, comments, and shares) was divided by the number of followers.
+This metric is often used to measure the level of audience interaction with a brand or organization on social media.
 
-## Material
-
-## Procedure
+## Overview of data analysis
+The data collected from this research instrument was analyzed using various statistical techniques, including descriptive statistics and …….
+Descriptive statistics were used to summarize the data and identify trends and patterns in the engagement rates, likes, comments, and shares for each post type and platform.
+In this analysis, we will examine the social media performance of the European Commission's Facebook, Instagram, Twitter, and Youtube accounts during the period from 24 March 2023 to 20 April 2023.
+We will focus on the engagement rate (ER) of each platform, which measures the percentage of followers who engage with a post by liking, commenting, sharing, or otherwise interacting with it.
 
 ## Data analysis
-We used `r cite_r("r-references.bib")` for all our analyses.
+We used `r cite_r("references.bib")` for all our analyses.
 

### 2023-04-22 Article.Rmd
corectat din nou

@@
 
-##Literature review
+## Literature review
+
 In the past few years, social media has risen to become a significant means of communication between public institutions and citizens.
@@
 ## Data analysis
-We used `r cite_r("references.bib")` for all our analyses.
+We used `r cite_r("r-references.bib")` for all our analyses.
 

### 2023-04-24 Article.Rmd
1

@@
   - id            : "1"
-    institution   : "Ovidius University, Constanța"
+    institution   : "Ovidius University, Constanța - Faculty of Law and Administrative Sciences"
   - id            : "2"
@@
 authornote: |
-  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
-
-  Enter author note here.
+  Department of Administrative and Social Sciences
 
@@
 ## Literature review
-
 In the past few years, social media has risen to become a significant means of communication between public institutions and citizens.

### 2023-04-24 analiza.R
25.04.2023

@@ -22,6 +22,10 @@ date %>%
   geom_text(position = position_stack(vjust = .5)) + theme_minimal() +
   ylab("World political leaders") + xlab("Number of posts") 
 
+ggplot(date, aes(Date, ER, colour=Page))+
+  geom_point() +
+  facet_wrap(~Page, ncol = 4, scales="free_x") + theme(legend.position = "none")
+
 #Tonul mesajelor - pozitiv vs. negativ####
 date$Message <- gsub("@[[:alpha:]]*","", date$Message)
 text_corpus <- Corpus(VectorSource(date$Message))
@@ -106,11 +110,11 @@ mean_ER <- data.frame(Platforma = c("Facebook", "Instagram", "Twitter", "YouTube
 barplot(mean_ER$Media_ER, names.arg = mean_ER$Platforma, col = "blue",
         xlab = "Platforme sociale", ylab = "Media rata de angajament (ER)")
 
-model <- lm(SentimentGI ~ Reactions + Likes + Comments + Shares, data = date)
+model <- lm(ER ~ SentimentGI, data = date)
 model
 
 library(ggplot2)
-ggplot(data = date, aes(x = SentimentGI, y = ER)) +
+ggplot(data = date, aes(x = SentimentGI, y = ER, colour=Page)) +
   geom_point() +
   geom_smooth(method = "lm", se = FALSE, color = "red") +
   labs(title = "Relația dintre scorul de sentiment și rata de angajament",

### 2023-04-27 analiza.R
27.04.2023

@@ -7,7 +7,7 @@ facebook <- read_xlsx("facebook.xlsx"); facebook$Page <- "Facebook"; facebook$ER
 twitter <- read_xlsx("twitter.xlsx"); twitter$Page <- "Twitter"; twitter$ER = twitter$Reactions/twitter$Fans; twitter <- select(twitter, Page, Message, Type, Date, Reactions, Likes, Comments, Shares, Fans, ER)
 instagram <- read_xlsx("instagram.xlsx"); instagram$Page <- "Instagram"; instagram$ER = instagram$Reactions/instagram$Fans; instagram <- select(instagram, Page, Message, Type, Date, Reactions, Likes, Comments, Shares, Fans, ER)
 youtube <- read_xlsx("youtube.xlsx"); youtube$Page <- "Youtube"; youtube$ER = youtube$Reactions/youtube$Fans; youtube <- select(youtube, Page, Message, Type, Date, Reactions, Likes, Comments, Shares, Fans, ER)
-date <- rbind(facebook,twitter, youtube,instagram); date <- filter(date, Date >= as.Date("2022-02-24"), Date <= as.Date("2023-04-23"))
+date <- rbind(facebook,twitter, youtube,instagram); date <- filter(date, Date >= as.Date("2020-01-01"), Date <= as.Date("2023-04-23"))
 
 #Salvare set de date####
 write_xlsx(x = date, path = "date.xlsx", col_names = TRUE); 

### 2023-05-18 Article.Rmd
Univariate

@@
 ```{r setup, include = FALSE}
-  library(papaja)
+  library(papaja); library(knitr); library(readxl); library(dplyr); library(psych)
+  library(sasLM);library(rstatix); library(naniar); library(lubridate); library(flextable)
+
   r_refs("r-references.bib")
@@
 To collect this data, the Fanpagekarma  platform was used, which is a popular tool for social media analytics and monitoring.
+
 The data extracted from the platform included the post ID, message content, post type, post date, number of likes, comments, shares, and rounded number of followers for each post made by the European Commission between 24 March 2023 and 20 April 2023.
+
 To calculate the engagement rate, the total number of reactions (likes, comments, and shares) was divided by the number of followers.
@@
 Descriptive statistics were used to summarize the data and identify trends and patterns in the engagement rates, likes, comments, and shares for each post type and platform.
+
 In this analysis, we will examine the social media performance of the European Commission's Facebook, Instagram, Twitter, and Youtube accounts during the period from 24 March 2023 to 20 April 2023.
@@
 
-## Data analysis
 We used `r cite_r("r-references.bib")` for all our analyses.

### 2023-05-18 01 - Descriptive analysis.R

@@ -1,0 +1,119 @@
+# Installing and loadinng required libraries
+if(!require(psych)) install.packages("psych")
+if(!require(sasLM)) install.packages("sasLM")
+if(!require(dplyr)) install.packages("dplyr")
+if(!require(rstatix)) install.packages("rstatix")
+if(!require(naniar)) install.packages("naniar")
+if(!require(lubridate)) install.packages("lubridate")
+if(!require(flextable)) install.packages("flextable")
+
+library(dplyr); library(psych); library(sasLM); library(rstatix); library(naniar)
+library(lubridate); library(flextable)
+
+# Loading dataset and computing ER
+load(file = "Raw data.RData"); head(ds)
+ds$ER = ds$Reactions / ds$Fans; ds <- ds %>% filter(ER != Inf)
+
+# Outliers detection and treatment ####
+tmp <- ds %>% filter(Page == "Facebook")
+out <- tmp %>% rstatix::identify_outliers(ER); out <- out[, c('ER', 'is.extreme')]
+colnames(out) <- c("Values", "Extreme"); out[out$Extreme == "TRUE",]
+boxplot(tmp$ER, horizontal = T, col = "dark green", outline = T)
+mtext(paste("Outliers: ", paste(out$Values, collapse=", ")), cex=0.6)
+tmp$ER[which(tmp$ER >= .00484)] <- NA
+ds.pur <- tmp
+
+tmp <- ds %>% filter(Page == "Instagram")
+out <- tmp %>% rstatix::identify_outliers(ER); out <- out[, c('ER', 'is.extreme')]
+colnames(out) <- c("Values", "Extreme"); out[out$Extreme == "TRUE",]
+boxplot(tmp$ER, horizontal = T, col = "dark green", outline = T)
+mtext(paste("Outliers: ", paste(out$Values, collapse=", ")), cex=0.6)
+tmp$ER[which(tmp$ER >= .0215)] <- NA
+ds.pur <- rbind(ds.pur, tmp)
+
+tmp <- ds %>% filter(Page == "Twitter")
+out <- tmp %>% rstatix::identify_outliers(ER); out <- out[, c('ER', 'is.extreme')]
+colnames(out) <- c("Values", "Extreme"); out[out$Extreme == "TRUE",]
[…]

### 2023-05-18 01 - Descriptive analysis.R
Analiza de sentiment

@@ -12,7 +12,7 @@ library(lubridate); library(flextable)
 
 # Loading dataset and computing ER
 load(file = "Raw data.RData"); head(ds)
-ds$ER = ds$Reactions / ds$Fans; ds <- ds %>% filter(ER != Inf)
+ds$ER = ds$Reactions / ds$Fans; ds <- ds %>% filter(ER != Inf); save(ds, file = "Raw data.RData")
 
 # Outliers detection and treatment ####
 tmp <- ds %>% filter(Page == "Facebook")

### 2023-05-19 analiza.R
1

@@ -9,6 +9,7 @@ instagram <- read_xlsx("instagram.xlsx"); instagram$Page <- "Instagram"; instagr
 youtube <- read_xlsx("youtube.xlsx"); youtube$Page <- "Youtube"; youtube$ER = youtube$Reactions/youtube$Fans; youtube <- select(youtube, Page, Message, Type, Date, Reactions, Likes, Comments, Shares, Fans, ER)
 date <- rbind(facebook,twitter, youtube,instagram); date <- filter(date, Date >= as.Date("2022-02-24"), Date <= as.Date("2023-04-23"))
 
+
 #Salvare set de date####
 write_xlsx(x = date, path = "date.xlsx", col_names = TRUE); 
 

### 2023-05-19 02 - Sentiment analysis.R
Last version

@@ -14,7 +14,7 @@ tc <- tm_map(tc, removeWords, stopwords("english")); tc <- tm_map(tc, removePunc
 ## Updating Message field in main dataset
 ds$Message  <- data.frame(Message = get("content", tc), stringsAsFactors = FALSE)$Message
 ## Doing sentiment analysis and updating main dataset
-ds <- cbind(ds, analyzeSentiment(ds$Message)); save(ds, file = "Row Sentiment.RData")
+ds <- cbind(ds, analyzeSentiment(ds$Message)); save(ds, file = "Raw Sentiment.RData")
 ## Plotting sentiment data
 names(ds); rm(tc)
 ggplot(data = ds, aes(x = Page, y = ER, fill=Page)) + 

### 2023-05-19 03 - Regressions.R

@@ -1,0 +1,83 @@
+# Installing and loading libraries
+if(!require(dplyr)) install.packages("dplyr")
+if(!require(caret)) install.packages("caret")
+if(!require(rstatix)) install.packages("rstatix")
+if(!require(lm.beta)) install.packages("lm.beta")
+if(!require(relaimpo)) install.packages("relaimpo")
+if(!require(ggpubr)) install.packages("ggpubr")
+if(!require(nortest)) install.packages("nortest")
+
+library(dplyr); library(caret); library(rstatix); library(ggpubr); library(lm.beta)
+library(relaimpo); library(nortest)
+
+
+# Function for p-values management ####
+p <- function(x, digits = 3){
+  if (x < 10^-digits) return(paste('<', 10^-digits))
+  paste('=', round(x, 3))}
+
+# Loading datasets ####
+load(file = "Raw Sentiment.RData"); load(file = "Pure Sentiment.RData"); head(ds)
+
+# Preparing datasets
+set.seed(453447)
+selection <- ds.pur$ER %>% createDataPartition(p = 0.8, list = FALSE)
+ds.estim  <- ds.pur[selection, ]; ds.asses <- ds.pur[-selection, ]; rm(selection)
+ds.estim$Set <- "Estimation"; ds.asses$Set <- "Assessment"
+ds.pur <- rbind(ds.estim, ds.asses); ds.pur$Set <- factor(ds.pur$Set); names(ds.pur)
+
+# Descriptive analysis on estimation and assessment sets ####
+ds.estim %>% get_summary_stats(type = "full", show = c("n", "min", "max", "median", "mean", "sd"))
+ds.asses %>% get_summary_stats(type = "full", show = c("n", "min", "max", "median", "mean", "sd"))
+t_test(ER ~ Set, data = ds.pur); t_test(NegativityGI ~ Set, data = ds.pur)
+
+ds.estim <- ds.pur
+# Assumptions assessment ####
+## I. Normality of dependent variable
+ad.test(ds.estim$ER)
+out <- ds.estim %>% identify_outliers(ER); out <- out[, c('ER', 'is.extreme')]; 
+range(out[out$is.extreme == "TRUE",]$ER)
+
+ggqqplot(ds.estim, x="ER", bxp.errorbar = T,
+         xlab = "Theoretical normal", ylab = "Empirical ER distribution")
[…]

### 2023-05-19 00 - Data processing.R
Regresie cu tot cu efectul paginii

@@ -14,7 +14,7 @@ if (!require(dplyr)) install.packages("dplyr")
 # if (!require(ggplot2)) install.packages("ggplot2")
 # if (!require(lubridate)) install.packages("lubridate")
 # if (!require(scales)) install.packages("scales")
-# if (!require(SentimentAnalysis)) install.packages("SentimentAnalysis")
+
 
 library(readxl); library(dplyr)
 # library(writexl); library(tidytext); library(tidyverse); library(tm); library(textdata)

### 2023-05-19 01 - Descriptive analysis.R

@@ -51,7 +51,7 @@ ds.pur <- rbind(ds.pur, tmp)
 rm(out, tmp); miss <- miss_var_summary(ds.pur); miss
 colnames(miss) <- c("Variable", "N", "%")
 ## Select only complete cases
-complete <- ds.pur[complete.cases(ds.pur),]
+#complete <- ds.pur[complete.cases(ds.pur),]
 complete <- ds.pur %>% dplyr::filter(!is.na(ER))
 loss <- nrow(ds.pur) - nrow(complete); ds.pur <- complete
 prc.miss <- as.numeric(round(miss[4,3], 2)); rm(complete, miss)
@@ -115,5 +115,3 @@ print.univar$Shapiro <- NULL; print.univar$p <- NULL;print.univar$R <- NULL
 print.univar$`SE Skew` <- NULL; print.univar$`SE Kurt` <- NULL
 colnames(print.univar) <- c("Variables", "N", "Mean", "SD", "Median", "Min", "Max","Skew (SE)", "Kurt (SE)")
 flextable(print.univar) %>% theme_apa() %>% save_as_docx(path = "Documents/Tab_Univariates_Pure.docx")
-
-

### 2023-05-19 02 - Sentiment analysis.R

@@ -1,7 +1,9 @@
 # Installing and loading libraries
 if (!require(tm)) install.packages("tm")
+if (!require(SentimentAnalysis)) install.packages("SentimentAnalysis")
+if (!require(ggplot2)) install.packages("ggplot2")
 
-library(tm)
+library(tm); library(SentimentAnalysis); library(ggplot2)
 
 # Loading datasets
 load(file = "Raw data.RData"); load(file = "Pure data.RData"); head(ds)
@@ -23,7 +25,7 @@ ggplot(data = ds, aes(x = Page, y = ER, fill=Page)) +
   theme_minimal()
 ggplot(ds, aes(Date, SentimentGI)) + geom_bin2d(colour="blue") + 
   scale_fill_gradient(low="light blue", high="dark blue") +
-  geom_hline(yintercept=0, linetype="dashed", color = "red", size = 1.5) +
+  geom_hline(yintercept = 0, linetype = "dashed", color = "red", size = 1.5) +
   ylab("Sentiment Indicator Values (Harvard-IV dictionary)") + xlab("Months") +
   facet_wrap(~Page, ncol = 4, scales="free_x") + theme_minimal() + theme(legend.position = "none")
 

### 2023-05-19 03 - Regressions.R

@@ -10,7 +10,6 @@ if(!require(nortest)) install.packages("nortest")
 library(dplyr); library(caret); library(rstatix); library(ggpubr); library(lm.beta)
 library(relaimpo); library(nortest)
 
-
 # Function for p-values management ####
 p <- function(x, digits = 3){
   if (x < 10^-digits) return(paste('<', 10^-digits))
@@ -29,13 +28,13 @@ ds.pur <- rbind(ds.estim, ds.asses); ds.pur$Set <- factor(ds.pur$Set); names(ds.
 # Descriptive analysis on estimation and assessment sets ####
 ds.estim %>% get_summary_stats(type = "full", show = c("n", "min", "max", "median", "mean", "sd"))
 ds.asses %>% get_summary_stats(type = "full", show = c("n", "min", "max", "median", "mean", "sd"))
-t_test(ER ~ Set, data = ds.pur); t_test(NegativityGI ~ Set, data = ds.pur)
+t_test(ER ~ Set, data = ds.pur); t_test( ~ Set, data = ds.pur); t_test(PositivityGI ~ Set, data = ds.pur)
 
-ds.estim <- ds.pur
+# ds.estim <- ds.pur
 # Assumptions assessment ####
 ## I. Normality of dependent variable
 ad.test(ds.estim$ER)
-out <- ds.estim %>% identify_outliers(ER); out <- out[, c('ER', 'is.extreme')]; 
+out <- ds.estim %>% identify_outliers(ER); out <- out[, c('ER', 'is.extreme')]
 range(out[out$is.extreme == "TRUE",]$ER)
 
 ggqqplot(ds.estim, x="ER", bxp.errorbar = T,
@@ -51,6 +50,10 @@ ggplot(ds.estim, aes(y = ER, x = PositivityGI)) +
 
 # Regression analysis ####
 mod <- lm(ER ~ NegativityGI + PositivityGI, 
+          data = ds.estim); mod.std <- lm.beta(mod); summary(mod.std)
+
+ds.estim$Page <- factor(ds.estim$Page, levels = c("Twitter", "Facebook", "Instagram", "Youtube"))
+mod <- lm(ER ~ NegativityGI + PositivityGI + factor(Page), 
           data = ds.estim); mod.std <- lm.beta(mod); summary(mod.std)
 
 # Relative predictors importance ####

### 2023-06-07 03 - Regressions.R
Versiunea 7 iunie

@@ -84,3 +84,4 @@ diag.mod %>% filter(abs(.hat) > 0.037)
 plot(mod, 4); diag.mod %>% top_n(4, wt = .cooksd)
 # Multicolinearity analysis
 car::vif(mod)
+

### 2023-06-07 Article.Rmd
The present study setup
literature review - refacut

@@
 ## Literature review
-In the past few years, social media has risen to become a significant means of communication between public institutions and citizens.
-This has paved the way for increased citizen engagement in the decision-making process, which is considered essential for fostering trust and enhancing accountability.
-This literature review delves into the significance of citizen involvement in the communication process of public institutions via social media.
-It does so by amalgamating and synthesizing the findings of diverse studies, each focusing on various facets of social media and citizen engagement within the European Union.
+In studying the impact of citizen engagement on the European Commission's social media platforms, it is crucial to discern the key concepts that underpin this research.
+These concepts are engagement, social media platforms, and sentiment analysis, which form the backbone of many academic discourses that revolve around these themes.
 
-@Bene2022 conducted a study exploring the impacts of self-centered social media communication styles on user engagement across 12 European nations.
-Their findings revealed that social media communication emphasizing user participation and fostering feedback effectively boosts user engagement.
-Social media users who feel they have a say in the decision-making process are more inclined to engage and participate in conversations.
-@DeWilde2022 examined citizen engagement with European politics on social media platforms and discovered that social media holds the potential to increase citizen involvement and participation in the political sphere.
-They found that social media offers citizens a platform to express their opinions, partake in discussions, and influence policy-making decisions.
-In a similar vein, @Bankston2021 investigated the role of social media in migration and smuggling across the European Union's virtual borders.
-This study concluded that social media platforms offer citizens opportunities to engage in dialogues and share their perspectives on immigration policies.
+Engagement, defined as the active interaction of users with digital content, is a fundamental element of any effective social media strategy.
+It encapsulates various forms of participation, from comments and shares to likes and views [@Mirbagheri2019].
+@Smith2015 argue that engagement helps in establishing profound relationships with users, and it can vary according to the type of platform [@Voorveld2018].
+The concept has found applicability in numerous contexts, including public health [@heldmanSocialMediaEngagement2013], student learning (Dragseth, 2020), and corporate social responsibility (@doncel-martinCorporateSocialResponsibility2023].
 
-@Cinelli2022, on the other hand, delved into promoting engagement with quality communication in social media.
-Their findings indicated that employing persuasive language, evoking emotions, and utilizing framing can enhance user engagement.
-The study recommends that public institutions implement quality communication techniques to boost citizen engagement and participation in policy-making.
-@Muller2022 analyzed the social media attention garnered by European Union agencies and found a positive correlation between increased attention and higher levels of citizen engagement.
-This study implies that public institutions can augment citizen engagement by effectively utilizing social media to showcase their activities and interact with citizens.
+The significance of engagement reaches a higher dimension in the political and public sphere.
+With social media platforms becoming an integral part of contemporary political communication [@flewPopulismGlobalisationSocial2020; @krzyzanowskiDigitalDiplomacyPolitical2020], citizen engagement has become paramount, as seen in the activities of European Union (EU) agencies (@Muller2022].
+There is a myriad of ways in which citizens engage with politics on social media, from commenting on posts to sharing and liking content [@DeWilde2022].
+This interaction has been correlated with a spectrum of outcomes, such as influencing voting behavior [@marquartThisTimeNot2020] and attitudes towards vaccination [@mascheriniSocialMediaUse2022].
 
-Additionally, @Rus2021 carried out a case study investigating the representation of the European Commission in Romania via social media communication.
-The study established that social media communication by public institutions can bolster transparency and accountability, consequently leading to heightened citizen engagement.
-@Hancu2020 examined the communication strategies employed by audit institutions in the European Union during the Covid-19 crisis.
-Their findings suggested that social media can serve as a potent tool for promoting public services and encouraging environmental engagement.
-The study advocates for public institutions to harness social media to showcase their activities and connect with citizens during times of crisis.
-@Kanol2021 scrutinized the social media engagement tactics of British interest groups on Facebook.
-They found that group type influences social media engagement strategies, with non-profit groups being more inclined to utilize user-generated content and participatory approaches.
-The study implies that public institutions can adopt lessons from non-profit groups and employ participatory strategies to elevate citizen engagement.
+Simultaneously, social media platforms are becoming recognized as powerful tools for promoting and managing engagement.
+This dual role is exemplified in the case of the European Commission's activities in Romania [@Rus2021].
+Recognizing the potential of these platforms to facilitate citizen engagement, EU institutions have taken steps to optimize their use, implementing various strategies [@Bene2022; @Kanol2021; @ozdemirBirdEyeView2022].
 
-Finally, @Wei2021 executed a case study analyzing public opinions on climate change policy in the European Union using Twitter data.
-The study concluded that social media offers a platform for citizens to discuss climate change policies, suggesting that public institutions should leverage social media to engage with citizens on critical issues like climate change.
+In assessing the impact of citizen engagement on the EU's social media platforms, researchers employ an assortment of methods, one of which is sentiment analysis.
+This approach, which involves the systematic identification and categorization of the emotional tone behind words, aims to gauge public sentiment, attitudes, and emotions towards specific topics [@Wei2021].
+It has been applied in diverse contexts, such as analyzing the emotional distribution in EU smart city communication [@kowalikSocialMediaDistribution2021] and exploring public opinions on climate change policy [@Wei2021].
+
+The European Union’s social media landscape is remarkably complex, as shown by numerous studies.
+These platforms can simultaneously facilitate positive engagement, such as public service promotion [@Hancu2020], and breed negative phenomena like hate speech [@doncel-martinCorporateSocialResponsibility2023] and digital vigilantism [@allenDigitalVigilantismSocial2020].
+Furthermore, the influence of these platforms is shaped by broader societal and political developments, such as migration and smuggling across virtual borders [@Bankston2021].
+
+To sum up, understanding the impact of citizen engagement on the European Commission's social media platforms is a multifaceted issue.
+These platforms offer opportunities for meaningful citizen engagement and public communication, but their influence is dictated by a complex interplay of individual behavior, institutional strategy, societal trends, and technological developments.
+This complexity calls for a nuanced understanding of each constituent factor and their collective role in shaping the landscape of citizen engagement within the context of the European Commission's social media platforms.
+It is a call to researchers, policymakers, and practitioners to continuously explore this evolving realm to maximize the benefits of citizen engagement while mitigating its potential pitfalls.
 
@@
 ## Research objectives
-The overall objective of this research is to analyze and compare the online engagement of the public on various official social media platforms (Facebook, Instagram, Twitter, and YouTube) of the European Commission.
+The primary objective of this research is to conduct a quantitative and qualitative analysis of public engagement across various official European Commission social media platforms (Facebook, Instagram, Twitter, and YouTube).
+This will involve comparing and contrasting the patterns, trends, and characteristics of online user interactions and responses across these platforms.
 
-## Research tool
-The research instrument used in this study involved the extraction and analysis of data from the official Facebook, Twitter, Instagram, and Youtube pages of the European Commission.
-To collect this data, the Fanpagekarma  platform was used, which is a popular tool for social media analytics and monitoring.
+## Research method
+The research methodology employed in this study involved the extraction and subsequent analysis of data derived from the official Facebook, Twitter, Instagram, and YouTube channels of the European Commission.
+To amass this data, we utilized the Fanpagekarma platform, a prevalent tool for conducting analytics and monitoring on social media platforms.
 
-The data extracted from the platform included the post ID, message content, post type, post date, number of likes, comments, shares, and rounded number of followers for each post made by the European Commission between 24 March 2023 and 20 April 2023.
+The data procured from this platform encompassed a range of elements, including post ID, message content, post type, post date, number of likes, comments, shares, and the rounded figure of followers for each post made by the European Commission in the period from the 3rd of February 2019 to the 23rd of April 2023.
 
-To calculate the engagement rate, the total number of reactions (likes, comments, and shares) was divided by the number of followers.
-This metric is often used to measure the level of audience interaction with a brand or organization on social media.
+In order to quantify the engagement rate, we calculated the total number of reactions (comprising likes, comments, and shares), and divided it by the total follower count.
+This engagement rate metric is commonly employed to gauge the extent of audience interaction with a brand or organization on social media platforms.
+To achieve the research objective, we employed a sentiment analysis method.
+
+## The present study
+H1: Communications with emotional resonance are associated with higher public engagement levels.
+H2: The effect of emotional resonance on public engagement is moderated by the social media platform utilized.
 
@@
 
-In this analysis, we will examine the social media performance of the European Commission's Facebook, Instagram, Twitter, and Youtube accounts during the period from 24 March 2023 to 20 April 2023.
+In this analysis, we will examine the social media performance of the European Commission's Facebook, Instagram, Twitter, and Youtube accounts during the period from `3 February 2019 to 23 April 2023.
 We will focus on the engagement rate (ER) of each platform, which measures the percentage of followers who engage with a post by liking, commenting, sharing, or otherwise interacting with it.

### 2023-06-07 Article.Rmd
Regression analysis

--- 2023-05-18 Article.Rmd
@@
 
+## The present study
+
 ## Overview of data analysis
+We used `r cite_r("r-references.bib")` for all our analyses.
+
+The initial assumptions assessment was performed by descriptive univariate analysis, data screening for outliers, and missing cases analysis, to verify univariate normality.
+Finally, a sentiment analysis was performed, and various comparative and regressive techniques was used for hypothesis testing.
+
 The data collected from this research instrument was analyzed using various statistical techniques, including descriptive statistics and …….
@@
 We will focus on the engagement rate (ER) of each platform, which measures the percentage of followers who engage with a post by liking, commenting, sharing, or otherwise interacting with it.
-
-We used `r cite_r("r-references.bib")` for all our analyses.
 

### 2023-06-07 03 - Regressions.R

@@ -25,21 +25,23 @@ ds.estim  <- ds.pur[selection, ]; ds.asses <- ds.pur[-selection, ]; rm(selection
 ds.estim$Set <- "Estimation"; ds.asses$Set <- "Assessment"
 ds.pur <- rbind(ds.estim, ds.asses); ds.pur$Set <- factor(ds.pur$Set); names(ds.pur)
 
+# ds.estim <- ds.pur
+# Assumptions assessment ####
+## I. Normality of dependent variable
+ds.estim <- ds.estim %>% dplyr::filter(ER != 0); ad.test(ds.estim$ER)
+out <- ds.estim %>% identify_outliers(ER); out <- out[, c('ER', 'is.extreme')]; out
+range(out[out$is.extreme == "TRUE",]$ER)
+ds.estim <- ds.estim %>% dplyr::filter(ER <= 0.000929525)
+
+ggqqplot(ds.estim, x="ER", bxp.errorbar = T,
+         xlab = "Theoretical normal", ylab = "Empirical ER distribution")
+plot(density(ds.estim$ER), ylab="Frequency"); polygon(density(ds.estim$ER), col = "dark green")
+
 # Descriptive analysis on estimation and assessment sets ####
 ds.estim %>% get_summary_stats(type = "full", show = c("n", "min", "max", "median", "mean", "sd"))
 ds.asses %>% get_summary_stats(type = "full", show = c("n", "min", "max", "median", "mean", "sd"))
 t_test(ER ~ Set, data = ds.pur); t_test( ~ Set, data = ds.pur); t_test(PositivityGI ~ Set, data = ds.pur)
 
-# ds.estim <- ds.pur
-# Assumptions assessment ####
-## I. Normality of dependent variable
-ad.test(ds.estim$ER)
-out <- ds.estim %>% identify_outliers(ER); out <- out[, c('ER', 'is.extreme')]
-range(out[out$is.extreme == "TRUE",]$ER)
-
-ggqqplot(ds.estim, x="ER", bxp.errorbar = T,
-         xlab = "Theoretical normal", ylab = "Empirical ER distribution")
-plot(density(ds.estim$ER), ylab="Frequency"); polygon(density(ds.estim$ER), col = "dark green")
 
 ## Liniarity check
 # 2. Analiza liniaritatii relatiei
@@ -80,6 +82,7 @@ par(mfrow = c(2, 2)); plot(mod)
[…]

### 2023-06-11 Article.Rmd

--- 2023-06-07 Article.Rmd
@@
 ## Overview of data analysis
+We used `r cite_r("r-references.bib")` for all our analyses.
+
+The initial assumptions assessment was performed by descriptive univariate analysis, data screening for outliers, and missing cases analysis, to verify univariate normality.
+Finally, a sentiment analysis was performed, and various comparative and regressive techniques was used for hypothesis testing.
+
 The data collected from this research instrument was analyzed using various statistical techniques, including descriptive statistics and …….

### 2023-06-11 Article.Rmd
Regression analysis

@@
     role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
+      - "Equal contribution"
       - "Conceptualization"
+      - "Data curation"
+      - "Investigation"
+      - "Formal analysis"
+      - "Resources"
+      - "Software"
+      - "Visualization"
       - "Writing - Original Draft Preparation"
@@
     role:
+      - "Equal contribution"
+      - "Writing - Original Draft Preparation"
       - "Writing - Review & Editing"
-      - "Supervision"
+      - "Data curation"
+      - "Formal analysis"
+      - "Resources"
+      - "Software"
+      - "Visualization"
+  - name          : "Cristina Dana Popescu"
+    affiliation   : "1"
+    role:
+      - "Writing - Original Draft Preparation"
+      - "Writing - Review & Editing"
+      - "Professional proofreading"
 
@@
   - id            : "1"
-    institution   : "Ovidius University, Constanța - Faculty of Law and Administrative Sciences"
+    institution   : "Ovidius University of Constanța, Romania"
   - id            : "2"
-    institution   : "Bucharest University"
+    institution   : "University of Bucharest, Romania"
 
@@
 
-# Case study
-## Research objectives
-The primary objective of this research is to conduct a quantitative and qualitative analysis of public engagement across various official European Commission social media platforms (Facebook, Instagram, Twitter, and YouTube).
-This will involve comparing and contrasting the patterns, trends, and characteristics of online user interactions and responses across these platforms.
+# The present study
+Relying on the theoretical framework previously described, the present study aimed to investigate public engagement across various official European Commission social media platforms (Facebook, Instagram, Twitter, and YouTube).
+We also compared and contrasted the patterns, trends, and characteristics of online user interactions and responses across these platforms.
+Translating these aims into research questions (RQs), the present study investigated the following:
 
-## Research method
-The research methodology employed in this study involved the extraction and subsequent analysis of data derived from the official Facebook, Twitter, Instagram, and YouTube channels of the European Commission.
-To amass this data, we utilized the Fanpagekarma platform, a prevalent tool for conducting analytics and monitoring on social media platforms.
+- *RQ~1~*. How is the communication with emotional resonance associated with higher public engagement levels?
+- *RQ~2~*. Does social media platforms influences the emotional resonance on public engagement?
+- *RQ~3~*. Does social media platforms moderates the effect of emotional resonance on public engagement?
 
-The data procured from this platform encompassed a range of elements, including post ID, message content, post type, post date, number of likes, comments, shares, and the rounded figure of followers for each post made by the European Commission in the period from the 3rd of February 2019 to the 23rd of April 2023.
+To answer these questions, we assumed the following:
 
-In order to quantify the engagement rate, we calculated the total number of reactions (comprising likes, comments, and shares), and divided it by the total follower count.
-This engagement rate metric is commonly employed to gauge the extent of audience interaction with a brand or organization on social media platforms.
-To achieve the research objective, we employed a sentiment analysis method.
+- *H~1~*: Communications with emotional resonance are associated with higher public engagement levels.
+- *H~2~*: Social media platform influences the emotional resonance on public engagement.
+- *H~3~*: The effect of emotional resonance on public engagement is moderated by the social media platform utilized.
 
-## The present study
-H1: Communications with emotional resonance are associated with higher public engagement levels.
-H2: The effect of emotional resonance on public engagement is moderated by the social media platform utilized.
+The novelty of our study lies in the fact that (1) **[TASE]**
 
+# Method
+## Procedure used for data gathering
+```{r descriptives, echo=FALSE, include=FALSE}
+  source("01 - Descriptive analysis.R")
+```
+
+We used the Fanpagekarma, a prevalent tool for conducting analytics and monitoring on social media platforms to extract data for the official Facebook, Twitter, Instagram, and YouTube channels of the European Commission.
+The data included post ID, message content, post type, post date, number of likes, comments, shares, and the rounded figure of followers for each post made by the European Commission, in the period from `r dt.min` to `r dt.max`.
+
+The engagement rate metric is commonly employed to gauge the extent of audience interaction with a brand or organization on social media platforms, and total number of reactions (comprising likes, comments, and shares) were calculated, and divided by the total follower count.
+A sentiment analysis method was used on engagement rate to reveal the trends and a linear regression analysis was conducted to test the hypothesis.
+
+# Results
 ## Overview of data analysis
@@
 The initial assumptions assessment was performed by descriptive univariate analysis, data screening for outliers, and missing cases analysis, to verify univariate normality.
-Finally, a sentiment analysis was performed, and various comparative and regressive techniques was used for hypothesis testing.
+We further conducted a sentiment analysis, and, finally a linear moderated regression was used for hypothesis testing.
 
-The data collected from this research instrument was analyzed using various statistical techniques, including descriptive statistics and …….
-Descriptive statistics were used to summarize the data and identify trends and patterns in the engagement rates, likes, comments, and shares for each post type and platform.
+## Preliminary analysis
+Some extreme high values were identified on Facebook engagement rate (values over .00484), Instagram engagement rate (values over .0215), Twitter engagement rate (values over .000696) and Youtube engagement rate (values over .000962) and replaced with missing values, however only `r prc.miss`% scores were missing so we decided to remove entire cases.
 
-In this analysis, we will examine the social media performance of the European Commission's Facebook, Instagram, Twitter, and Youtube accounts during the period from `3 February 2019 to 23 April 2023.
-We will focus on the engagement rate (ER) of each platform, which measures the percentage of followers who engage with a post by liking, commenting, sharing, or otherwise interacting with it.
+```{r Descriptives-Table-Ext, echo=FALSE}
+   kable(print.univar.row, format = "latex", digits = 8, booktabs = T, caption = "Descriptive analysis. Presence of extreme outliersa")
+```
 
-# Results
+```{r Descriptives-Table-Pur, echo=FALSE}
+   kable(print.univar.pur, format = "latex", digits = 8, booktabs = T, caption = "Descriptive analysis. Extreme outliers removed")
+```
+
+Results suggested that all engagement rates were highly positively skewed and highly leptokurtic (see Tables \@ref(tab:Descriptives-Table-Ext) and \@ref(tab:Descriptives-Table-Pur)) and the univariate normality assumption of the dependent variable was not met.
+
+\center _Please Insert Tables \@ref(tab:Descriptives-Table-Ext) and \@ref(tab:Descriptives-Table-Pur) around here_ \justify
+
+```{r sentiment, echo=FALSE, include=FALSE}
+  source("02 - Sentiment analysis.R")
+```
+```{r, boxplot-EXT, out.width = '510px', fig.align='center', fig.cap='Boxplot of engagement rates on social media channels. Extremes included', warning=FALSE}
+  bp.ext
+```
+```{r, sent-EXT, out.width = '510px', fig.align='center', fig.cap='Sentiment analysis chart on social media channels. Extremes included', warning=FALSE}
+  st.ext
+```
+```{r, boxplot-NEXT, out.width = '510px', fig.align='center', fig.cap='Boxplot of engagement rates on social media channels. Extremes excluded', warning=FALSE}
+  bp.next
+```
+```{r, sent-NEXT, out.width = '510px', fig.align='center', fig.cap='Sentiment analysis chart on social media channels. Extremes excluded', warning=FALSE}
+  st.next
+```
+
+We further performed a sentiment analysis both on data with (see Fig.
+\@ref(fig:boxplot-EXT) and Fig.
+\@ref(fig:sent-EXT)) and without extreme outliers (see Fig.
+\@ref(fig:boxplot-NEXT) and Fig.
+\@ref(fig:sent-NEXT)) and the information suggested that ...
+**[TASE]**
+
+```{r prediction, echo=F, include=FALSE}
+  source("03 - Regressions.R")
+```
+
+Finally, a linear regression model was fitted using `r est.n` cases from the purified dataset, values on engagement rate over .000929525 were removed because of extreme outliers and the normality of dependent variable was not met (Anderson-Darling test =`r ad.stat`, p `r ad.p`).
+
+The results suggested that the null hypothesis **H~0~:** *Communications with emotional resonance are not associated with higher public engagement levels* could be rejected (F(`r m1.F.df1`, `r m1.F.df2`)=`r m1.F`, p `r m1.F.p`) and the *H~1~*: *Communications with emotional resonance are associated with higher public engagement levels* was plausible, however the engagement levels was explained only by `r m1.r2.p`% by the positive and negative resonance communications (R^2^=`r m1.r2`, RSR=`r m1.RSE`).
+
+The positive *(B=`r m1.poz.B`, t=`r m1.poz.t`, p  `r m1.poz.p`, \(\beta\)=`r m1.poz.Bt`)* and negative *(B=`r m1.neg.B`, t=`r m1.neg.t`, p  `r m1.neg.p`, \(\beta\)=`r m1.neg.Bt`)* emotional resonance communications were both positively associated statistically significant with engagement rates, and high values on emotional resonance, positive or negative, were associated with high values on engagement rates.
+However, the relative predictors relevance showed that negative emotional resonance (`r m1.neg.lmg`%) contributed more on engagement rates explanation than positive emotional resonance (`r m1.poz.lmg`%)
+
+Furthermore, we observed that the effect of social media platform was statistically significant on all platforms compared with Twitter and the null hypothesis **H~0~:** *The effect of emotional resonance on public engagement is not moderated by the social media platform* could be rejected.
+(F(`r m2.F.df1`, `r m2.F.df2`)=`r m2.F`, p `r m2.F.p`).
+Adding the new as categorical predictor increased the prediction power at `r m2.r2.p`% from `r m1.r2.p`% (R^2^=`r m2.r2`, RSR=`r m2.RSE`), as the most relevant predictor was social network (`r m2.fac.lmg`%), followed by negative emotional resonance (`r m2.neg.lmg`%) and positive emotional resonance (`r m2.poz.lmg`%)
+
+Negative emotional resonance was still statistically significant positively associated by public engagement *(B=`r m2.neg.B`, t=`r m2.neg.t`, p  `r m2.neg.p`, \(\beta\)=`r m2.neg.Bt`)*, but not positive emotional resonance *(B=`r m2.poz.B`, t=`r m2.poz.t`, p  `r m2.poz.p`, \(\beta\)=`r m2.poz.Bt`)*, and compared by Twitter, engagement rates increased statistically significant on Facebook *(B=`r m2.Fcb.B`, t=`r m2.Fcb.t`, p  `r m2.Fcb.p`, \(\beta\)=`r m2.Fcb.Bt`)*, Instagram *(B=`r m2.Isg.B`, t=`r m2.Isg.t`, p  `r m2.Isg.p`, \(\beta\)=`r m2.Isg.Bt`)* and Youtube *(B=`r m2.Ytb.B`, t=`r m2.Ytb.t`, p  `r m2.Ytb.p`, \(\beta\)=`r m2.Ytb.Bt`)*.
 

### 2023-06-11 02 - Sentiment analysis.R

@@ -16,18 +16,20 @@ tc <- tm_map(tc, removeWords, stopwords("english")); tc <- tm_map(tc, removePunc
 ## Updating Message field in main dataset
 ds$Message  <- data.frame(Message = get("content", tc), stringsAsFactors = FALSE)$Message
 ## Doing sentiment analysis and updating main dataset
-ds <- cbind(ds, analyzeSentiment(ds$Message)); save(ds, file = "Raw Sentiment.RData")
+#ds <- cbind(ds, analyzeSentiment(ds$Message)); save(ds, file = "Raw Sentiment.RData")
 ## Plotting sentiment data
-names(ds); rm(tc)
-ggplot(data = ds, aes(x = Page, y = ER, fill=Page)) + 
+load(file = "Raw Sentiment.RData"); names(ds); rm(tc)
+bp.ext <- ggplot(data = ds, aes(x = Page, y = ER, fill=Page)) + 
   geom_boxplot() + 
+  ylab("Engagement Rates. Extremes included") +
+  xlab("Social media page") +
   facet_wrap(~Page, ncol = 4, scales = "free_x")+
-  theme_minimal()
-ggplot(ds, aes(Date, SentimentGI)) + geom_bin2d(colour="blue") + 
+  theme_minimal(); bp.ext
+st.ext <- ggplot(ds, aes(Date, SentimentGI)) + geom_bin2d(colour="blue") + 
   scale_fill_gradient(low="light blue", high="dark blue") +
   geom_hline(yintercept = 0, linetype = "dashed", color = "red", size = 1.5) +
-  ylab("Sentiment Indicator Values (Harvard-IV dictionary)") + xlab("Months") +
-  facet_wrap(~Page, ncol = 4, scales="free_x") + theme_minimal() + theme(legend.position = "none")
+  ylab("Sentiment Values (Harvard-IV dictionary). Extremes included") + xlab("Months") +
+  facet_wrap(~Page, ncol = 4, scales="free_x") + theme_minimal() + theme(legend.position = "none"); st.ext
 
 # Sentiment analysis - Purified dataset ####
 ds.pur$Message <- gsub("@[[:alpha:]]*","", ds.pur$Message)
@@ -37,15 +39,17 @@ tc <- tm_map(tc, removeWords, stopwords("english")); tc <- tm_map(tc, removePunc
 ## Updating Message field in main dataset
[…]

### 2023-06-11 03 - Regressions.R

@@ -16,7 +16,7 @@ p <- function(x, digits = 3){
   paste('=', round(x, 3))}
 
 # Loading datasets ####
-load(file = "Raw Sentiment.RData"); load(file = "Pure Sentiment.RData"); head(ds)
+load(file = "Pure Sentiment.RData"); head(ds.pur)
 
 # Preparing datasets
 set.seed(453447)
@@ -28,11 +28,12 @@ ds.pur <- rbind(ds.estim, ds.asses); ds.pur$Set <- factor(ds.pur$Set); names(ds.
 # ds.estim <- ds.pur
 # Assumptions assessment ####
 ## I. Normality of dependent variable
-ds.estim <- ds.estim %>% dplyr::filter(ER != 0); ad.test(ds.estim$ER)
+ds.estim <- ds.estim %>% dplyr::filter(ER != 0)
 out <- ds.estim %>% identify_outliers(ER); out <- out[, c('ER', 'is.extreme')]; out
 range(out[out$is.extreme == "TRUE",]$ER)
 ds.estim <- ds.estim %>% dplyr::filter(ER <= 0.000929525)
-
+nor.test <- ad.test(ds.estim$ER); nor.test
+ad.stat <- round(nor.test$statistic); ad.p <- p(nor.test$p.value, digits = 3)
 ggqqplot(ds.estim, x="ER", bxp.errorbar = T,
          xlab = "Theoretical normal", ylab = "Empirical ER distribution")
 plot(density(ds.estim$ER), ylab="Frequency"); polygon(density(ds.estim$ER), col = "dark green")
@@ -40,8 +41,10 @@ plot(density(ds.estim$ER), ylab="Frequency"); polygon(density(ds.estim$ER), col 
 # Descriptive analysis on estimation and assessment sets ####
 ds.estim %>% get_summary_stats(type = "full", show = c("n", "min", "max", "median", "mean", "sd"))
 ds.asses %>% get_summary_stats(type = "full", show = c("n", "min", "max", "median", "mean", "sd"))
-t_test(ER ~ Set, data = ds.pur); t_test( ~ Set, data = ds.pur); t_test(PositivityGI ~ Set, data = ds.pur)
-
+ech.ER <- t_test(ER ~ Set, data = ds.pur); ech.ER
[…]

### 2023-06-11 Article.Rmd
1

--- 2023-06-11 Article.Rmd
@@
 The significance of engagement reaches a higher dimension in the political and public sphere.
-With social media platforms becoming an integral part of contemporary political communication [@flewPopulismGlobalisationSocial2020; @krzyzanowskiDigitalDiplomacyPolitical2020], citizen engagement has become paramount, as seen in the activities of European Union (EU) agencies (@Muller2022].
+With social media platforms becoming an integral part of contemporary political communication [@flewPopulismGlobalisationSocial2020; @krzyzanowskiDigitalDiplomacyPolitical2020], citizen engagement has become paramount, as seen in the activities of European Union (EU) agencies [@Muller2022].
 There is a myriad of ways in which citizens engage with politics on social media, from commenting on posts to sharing and liking content [@DeWilde2022].

### 2023-06-11 Article.Rmd
12.06.2023

@@
 shorttitle        : "Impact of Citizen Engagement on the European Commission's Social Media Platforms"
-
 author: 
@@
       - "Professional proofreading"
-
 affiliation:
@@
     institution   : "University of Bucharest, Romania"
-
 authornote: |
   Department of Administrative and Social Sciences
-
 abstract: |
-  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.
-
-  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.
-
-  One sentence clearly stating the **general problem** being addressed by  this particular study.
-
-  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).
-
-  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.
-
-  One or two sentences to put the results into a more **general context**.
-
-  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.
-
-  <!-- https://tinyurl.com/ybremelq -->
-
-keywords          : "keywords"
+  This study investigates the role of emotional resonance in social media communications from the European Commission (EC) and its impact on public engagement across different platforms (Facebook, Instagram, Twitter, and YouTube).
+Our results indicate that messages with emotional resonance significantly boost public engagement levels, with the effects varying based on the specific platform.
+We further reveal a notable influence of both positive and negative emotional resonance on engagement, with the latter exerting a stronger impact.
+This research expands our understanding of engagement dynamics on different platforms, stressing the importance of tailored platform-specific strategies.
+The findings underscore the crucial role of social media in enhancing public involvement in policy dialogue and emphasize the need for public institutions to incorporate emotional resonance into their communication strategies, accounting for unique platform characteristics.
+These insights provide a foundation for future discussions and research into optimizing communication strategies within a multi-platform environment, which will shape the future of digital governance and public policymaking.
+keywords          : "social media, public institutions, emotional resonance, public engagement, platform-specific strategies, digital governance"
 wordcount         : "X"
@@
 
-The novelty of our study lies in the fact that (1) **[TASE]**
+The novelty of our study lies in the fact that we have systematically compared and contrasted user engagement and emotional resonance across multiple social media platforms utilized by the European Commission.
+While previous research has generally focused on the impact of citizen engagement within a single social media platform, our study is unique in its comprehensive cross-platform analysis.
+
+In this context, we have pursued an integrated approach to understanding how emotional resonance can influence public engagement levels across these platforms.
+Furthermore, we have explored the moderating effect of the social media platform itself on the impact of emotional resonance, a novel aspect that has not been fully addressed in previous research.
+
+The innovative approach of this study allowed us to draw robust conclusions about the nuanced relationship between communication strategy, emotional resonance, platform choice, and public engagement.
+Our research has therefore not only provided key insights into the patterns of citizen engagement on European Commission's social media platforms, but also presented an advanced framework for understanding how such engagement can be effectively harnessed and maximized for public outreach and policymaking.
+
+Ultimately, this study has expanded the current discourse in the field of digital communication and citizen engagement, and opened up new avenues for future research on optimizing communication strategies in a multi-platform social media environment.
 
@@
 
-We further performed a sentiment analysis both on data with (see Fig.
+A comprehensive sentiment analysis was conducted on data, both with (see Fig.
 \@ref(fig:boxplot-EXT) and Fig.
@@
 \@ref(fig:boxplot-NEXT) and Fig.
-\@ref(fig:sent-NEXT)) and the information suggested that ...
-**[TASE]**
+\@ref(fig:sent-NEXT)) suggesting distinctive tonal variations in the discourse employed by the European Commission across different social media platforms.
+In the case of Facebook, the sentiment indicator's mean value was determined to be 0.14, indicative of a marginally positive tone.
+The sentiment ranged between -0.27 and 0.63.
+The discourse with a negative connotation averaged at -0.08, while the discourse with a positive undertone demonstrated a mean of 0.22, thereby further substantiating a propensity for positivity.
+
+Akin to Facebook, the sentiment indicator on Instagram averaged at 0.12, which points towards a mildly positive sentiment, with the spectrum extending from -0.22 to 0.46.
+The mean sentiment score for negatively perceived discourse was -0.07, and the positively perceived discourse showed an average of 0.20, once again suggesting a bend towards positive discourse on this platform.
+
+Conversely, Twitter displayed a broader sentiment spectrum.
+Although the sentiment indicator mean was marginally higher than Facebook and Instagram at 0.15, it ranged from -0.63 to 1.00, implying a more diverse expression of sentiments.
+Negative discourse manifested an average of -0.07, identical to Instagram but more negative than Facebook.
+Interestingly, Twitter maintained the highest average score for positive discourse, at 0.22, equal to the positivity in Facebook and surpassing that on Instagram.
+
+On YouTube, the sentiment indicator's mean value was observed to be the lowest amongst the evaluated platforms at 0.10, spanning from -0.19 to 0.34, thereby indicating a more tempered sentiment.
+Negative discourse on YouTube scored the lowest mean of -0.03, while positive discourse registered the minimum average of 0.13 compared to the other platforms.
+
+In conclusion, despite a general inclination towards a slightly positive mean sentiment across all platforms, Twitter demonstrated the most substantial sentiment range, signifying the potential for both intensely negative and positive discourse.
+Instagram and Facebook depicted a modestly positive sentiment with less variability, while YouTube exhibited the most tempered sentiment range, with the lowest averages for both positive and negative discourse.
 
@@
 # Discussion
+This investigation commenced with the aim of assessing the impact of citizen engagement on the European Commission's social media platforms by specifically evaluating the influence of emotionally resonant communications on public engagement levels.
+The discussion here explores the findings derived from the study and their implications, juxtaposing them against the extant body of research on social media engagement, public institutional communication, and the role of emotional resonance in these facets.
+
+The first hypothesis (H1) was predicated on the notion that communications with emotional resonance would yield higher public engagement levels.
+The research findings provided empirical support to this hypothesis, demonstrating a significant association between emotionally resonant communications and amplified levels of public engagement.
+This echoes previous scholarly work emphasizing the role of emotional appeal in enhancing audience engagement on social media platforms (Dolan et al., 2016; Smith & Gallicano, 2015).
+However, our research contributes a new dimension by bringing these aspects into the realm of public institutions, specifically the European Commission.
+
+Public institutions often struggle with perceived remoteness and disconnection from citizens.
+However, the advent of social media offers a new avenue for these institutions to reach out to their citizenry, thereby allowing them to foster greater trust and engagement.
+Our findings confirm that the integration of emotional resonance within these online communications could significantly enhance this engagement process, fostering a more meaningful and interactive dialogue between the institutions and citizens.
+
+Our findings align with the theoretical underpinnings of the uses and gratifications theory, emphasizing that emotional resonance serves as a primary motivation for users to engage with social media content.
+Consequently, public institutions should incorporate emotionally resonant messages into their social media communications to meet these user motivations, thus promoting higher engagement levels.
+This reflects the findings of Dolan et al.
+(2016), who identified emotional resonance as a key motivator in user engagement behavior.
+
+The second hypothesis (H2) postulated that the social media platform could exert an influence on the emotional resonance in public engagement.
+The findings of the study substantiated this claim, revealing that the type of social media platform indeed moderates the impact of emotional resonance on public engagement.
+This variability across platforms underscores the need for a more nuanced, platform-specific approach to communication strategies.
+
+Such an approach resonates with the findings of @Voorveld2018 who noted the differential roles of different social media platforms in user engagement.
+Public institutions, therefore, need to be mindful of these variations, ensuring that their communication strategies are tailored to the specific features, functionalities, and user behaviors of each platform to maximize the effectiveness of their emotionally resonant communications.
+
+Our third hypothesis (H3) proposed that the social media platform could moderate the effect of emotional resonance on public engagement.
+This hypothesis was also validated by the study, underscoring the pivotal role that the choice of the social media platform plays in shaping public engagement levels.
+Each platform presents unique attributes and user behaviors, influencing the extent to which emotional resonance can stimulate public engagement.
+
+This finding also converges with the research conducted by @Voorveld2018, which asserted the differentiating impact of platform type on social media engagement.
+Hence, the insights derived from our study reinforce the need for public institutions to strategically consider their choice of social media platform, factoring in the distinctive characteristics of each platform and their corresponding audience base to optimize their emotionally resonant communications.
+
+A particularly interesting revelation was the relative impact of positive and negative emotional resonance on engagement levels.
+Both types of emotional resonance were found to amplify engagement levels, yet negative emotional resonance appeared to exert a stronger influence.
+This suggests that audiences may be more inclined to engage with messages that evoke negative emotions.
+Public institutions must carefully navigate this complex terrain, ensuring that their communications strike a delicate balance between positive and negative emotional resonance, taking into consideration the potential risks and rewards of each approach.
+
+In sum, this study provides a wealth of empirical evidence to support the significance of emotional resonance in amplifying citizen engagement on the social media platforms of public institutions.
+It is a clarion call for public organizations to strategically incorporate emotional resonance into their communications, thereby leveraging this engagement driver to foster a more interactive, engaging dialogue with their audiences.
+Further, it highlights the pivotal role of platform choice, emphasizing the need to take into account the unique attributes and audiences of each platform in formulating and executing effective communication strategies.
+
+However, despite its contributions, this study is not without its limitations.
+Future research should delve deeper into the intricate relationship between emotional resonance and public engagement, examining potential moderating factors such as the type of communication, audience demographics, or the cultural context.
+Additionally, further studies could evaluate the differential impact of positive and negative emotional resonance, providing a more nuanced understanding of how these contrasting types of emotional appeal influence public engagement.
+The role of individual social media platforms and their unique features in shaping emotional resonance could also be explored in more detail, providing insights into how public institutions can optimize their platform-specific strategies.
+
+This research offers a critical springboard for public institutions to understand and leverage emotional resonance in their social media communications, thereby unlocking new opportunities for more effective and engaging citizen interactions.
+As public institutions continue to navigate the digital landscape, they must take these findings into account, recognizing the crucial role of emotional resonance in social media communications as well as the importance of adopting a platform-specific approach.
+The benefits of doing so will not only enhance public engagement but also foster a stronger, more trustful relationship between public institutions and their audiences.
 

### 2023-06-11 02 - Sentiment analysis.R

@@ -53,3 +53,5 @@ st.next <- ggplot(ds.pur, aes(Date, SentimentGI)) + geom_bin2d(colour="blue") +
   geom_hline(yintercept=0, linetype="dashed", color = "red", size = 1.5) +
   ylab("Sentiment Indicator Values (Harvard-IV dictionary). Extremes excluded") + xlab("Months") +
   facet_wrap(~Page, ncol = 4, scales="free_x") + theme_minimal() + theme(legend.position = "none"); st.next
+
+

### 2023-06-12 02 - Sentiment analysis.R
Minor changes

@@ -15,8 +15,9 @@ tc <- tm_map(tc, tolower); tc <- tm_map(tc, removeWords, c("rt", "re", "amp"))
 tc <- tm_map(tc, removeWords, stopwords("english")); tc <- tm_map(tc, removePunctuation)
 ## Updating Message field in main dataset
 ds$Message  <- data.frame(Message = get("content", tc), stringsAsFactors = FALSE)$Message
-## Doing sentiment analysis and updating main dataset
+## *******  Doing sentiment analysis and updating main dataset ********
 #ds <- cbind(ds, analyzeSentiment(ds$Message)); save(ds, file = "Raw Sentiment.RData")
+## ********************************************************************
 ## Plotting sentiment data
 load(file = "Raw Sentiment.RData"); names(ds); rm(tc)
 bp.ext <- ggplot(data = ds, aes(x = Page, y = ER, fill=Page)) + 
@@ -38,8 +39,9 @@ tc <- tm_map(tc, tolower); tc <- tm_map(tc, removeWords, c("rt", "re", "amp"))
 tc <- tm_map(tc, removeWords, stopwords("english")); tc <- tm_map(tc, removePunctuation)
 ## Updating Message field in main dataset
 ds.pur$Message  <- data.frame(Message = get("content", tc), stringsAsFactors = FALSE)$Message
-## Doing sentiment analysis and updating main dataset
+## ******* Doing sentiment analysis and updating main dataset ********
 #ds.pur <- cbind(ds.pur, analyzeSentiment(ds.pur$Message)); save(ds.pur, file = "Pure Sentiment.RData")
+## *******************************************************************
 ## Plotting sentiment data
 load(file = "Pure Sentiment.RData"); names(ds.pur); rm(tc)
 bp.next <- ggplot(data = ds.pur, aes(x = Page, y = ER, fill=Page)) + 

### 2023-06-12 Article.Rmd
sentiment analysis updated

@@
 ```
-
+## Sentiment analysis
 A comprehensive sentiment analysis was conducted on data, both with (see Fig.
@@
 \@ref(fig:sent-NEXT)) suggesting distinctive tonal variations in the discourse employed by the European Commission across different social media platforms.
-In the case of Facebook, the sentiment indicator's mean value was determined to be 0.14, indicative of a marginally positive tone.
-The sentiment ranged between -0.27 and 0.63.
-The discourse with a negative connotation averaged at -0.08, while the discourse with a positive undertone demonstrated a mean of 0.22, thereby further substantiating a propensity for positivity.
+
+\center _Please Insert Figures \@ref(fig:boxplot-EXT) and \@ref(fig:sent-EXT) around here_ \justify
+
+\center _Please Insert Figures \@ref(fig:boxplot-NEXT) and \@ref(fig:sent-NEXT) around here_ \justify
+
+In the case of Facebook, the sentiment's indicator mean value was `r fb.sent.mean.next` (SD=`r fb.sent.sd.next`), showed a tendency to a positive tone (M=`r fb.sent.mean.ext`, SD=`r fb.sent.sd.ext` with extreme outliers).
+The sentiment ranged between `r fb.sent.min.next` and `r fb.sent.max.next` (`r fb.sent.min.ext` and `r fb.sent.max.ext` with extreme outliers), the discourse with a negative connotation averaged at `r fb.neg.mean.next` (SD=`r fb.neg.sd.next`), while the discourse with a positive undertone demonstrated a mean of `r fb.poz.mean.next` (SD=`r fb.poz.sd.next`), thereby further substantiating a propensity for positivity (M=`r fb.neg.mean.ext`, SD=`r fb.neg.sd.ext`, respectively M=`r fb.poz.mean.ext`, SD=`r fb.poz.sd.ext` with extreme outliers).
 

### 2023-06-12 02 - Sentiment analysis.R

@@ -2,8 +2,9 @@
 if (!require(tm)) install.packages("tm")
 if (!require(SentimentAnalysis)) install.packages("SentimentAnalysis")
 if (!require(ggplot2)) install.packages("ggplot2")
+if (!require(dplyr)) install.packages("dplyr")
 
-library(tm); library(SentimentAnalysis); library(ggplot2)
+library(tm); library(SentimentAnalysis); library(ggplot2); library(dplyr)
 
 # Loading datasets
 load(file = "Raw data.RData"); load(file = "Pure data.RData"); head(ds)
@@ -20,6 +21,62 @@ ds$Message  <- data.frame(Message = get("content", tc), stringsAsFactors = FALSE
 ## ********************************************************************
 ## Plotting sentiment data
 load(file = "Raw Sentiment.RData"); names(ds); rm(tc)
+tmp <- ds %>%  dplyr::filter(Page == "Facebook")
+fb.sent.min.ext <- round(min(tmp$SentimentGI, na.rm = T), 5)
+fb.sent.max.ext <- round(max(tmp$SentimentGI, na.rm = T), 5)
+fb.sent.mean.ext <- round(mean(tmp$SentimentGI, na.rm = T), 5)
+fb.sent.sd.ext <- round(sd(tmp$SentimentGI, na.rm = T), 5)
+fb.neg.min.ext <- round(min(tmp$NegativityGI, na.rm = T), 5)
+fb.neg.max.ext <- round(max(tmp$NegativityGI, na.rm = T), 5)
+fb.neg.mean.ext <- round(mean(tmp$NegativityGI, na.rm = T), 5)
+fb.neg.sd.ext <- round(sd(tmp$NegativityGI, na.rm = T), 5)
+fb.poz.min.ext <- round(min(tmp$PositivityGI, na.rm = T), 5)
+fb.poz.max.ext <- round(max(tmp$PositivityGI, na.rm = T), 5)
+fb.poz.mean.ext <- round(mean(tmp$PositivityGI, na.rm = T), 5)
+fb.poz.sd.ext <- round(sd(tmp$PositivityGI, na.rm = T), 5)
+
+tmp <- ds %>%  dplyr::filter(Page == "Instagram")
[…]

### 2023-06-12 Article.Rmd
1

@@
 
-Akin to Facebook, the sentiment indicator on Instagram averaged at 0.12, which points towards a mildly positive sentiment, with the spectrum extending from -0.22 to 0.46.
-The mean sentiment score for negatively perceived discourse was -0.07, and the positively perceived discourse showed an average of 0.20, once again suggesting a bend towards positive discourse on this platform.
+In contrast to Facebook, the sentiment indicator on Instagram averaged at `r ig.sent.mean.next`, which points towards a mildly positive sentiment, with the spectrum extending from `r ig.sent.min.next` and `r ig.sent.max.next` (`r ig.sent.min.ext` and `r ig.sent.max.ext` with extreme outliers).
+The mean sentiment score for negatively perceived discourse was `r ig.neg.mean.next` (SD=`r ig.neg.sd.next`), and the positively perceived discourse showed an average of (M=`r ig.neg.mean.ext`, SD=`r ig.neg.sd.ext`, respectively M=`r ig.poz.mean.ext`, SD=`r fb.poz.sd.ext` with extreme outliers), once again suggesting a bend towards positive discourse on this platform.
 
 Conversely, Twitter displayed a broader sentiment spectrum.
-Although the sentiment indicator mean was marginally higher than Facebook and Instagram at 0.15, it ranged from -0.63 to 1.00, implying a more diverse expression of sentiments.
-Negative discourse manifested an average of -0.07, identical to Instagram but more negative than Facebook.
-Interestingly, Twitter maintained the highest average score for positive discourse, at 0.22, equal to the positivity in Facebook and surpassing that on Instagram.
+Although the sentiment indicator mean was marginally higher than Facebook and Instagram at `r tw.sent.mean.next`, it ranged from `r tw.sent.min.next` and `r tw.sent.max.next` (`r tw.sent.min.ext` and `r tw.sent.max.ext` with extreme outliers), implying a more diverse expression of sentiments.
+Negative discourse manifested an average of `r tw.neg.mean.next` (SD=`r tw.neg.sd.next`), identical to Instagram but more negative than Facebook.
+Interestingly, Twitter maintained the highest average score for positive discourse, at `r tw.poz.mean.ext` (SD=`r tw.poz.sd.ext` with extreme outliers), equal to the positivity in Facebook and surpassing that on Instagram.
 
-On YouTube, the sentiment indicator's mean value was observed to be the lowest amongst the evaluated platforms at 0.10, spanning from -0.19 to 0.34, thereby indicating a more tempered sentiment.
-Negative discourse on YouTube scored the lowest mean of -0.03, while positive discourse registered the minimum average of 0.13 compared to the other platforms.
+On YouTube, the sentiment indicator's mean value was observed to be the lowest amongst the evaluated platforms at `r yt.sent.mean.next`, spanning from `r yt.sent.min.next` and `r yt.sent.max.next` (`r yt.sent.min.ext` and `r yt.sent.max.ext` with extreme outliers), thereby indicating a more tempered sentiment.
+Negative discourse on YouTube scored the lowest mean of `r yt.neg.mean.next` (SD=`r yt.neg.sd.next`), while positive discourse registered the minimum average of `r yt.poz.mean.ext` (SD=`r yt.poz.sd.ext` with extreme outliers) compared to the other platforms.
 

### 2023-06-12 Article.Rmd
Moderation effect interpretation

--- 2023-06-12 Article.Rmd
@@
 
-Finally, a linear regression model was fitted using `r est.n` cases from the purified dataset, values on engagement rate over .000929525 were removed because of extreme outliers and the normality of dependent variable was not met (Anderson-Darling test =`r ad.stat`, p `r ad.p`).
+A linear regression model was fitted using `r est.n` cases from the purified dataset, values on engagement rate over .000929525 were removed because of extreme outliers and the normality of dependent variable was not met (Anderson-Darling test =`r ad.stat`, p `r ad.p`).
 
@@
 Negative emotional resonance was still statistically significant positively associated by public engagement *(B=`r m2.neg.B`, t=`r m2.neg.t`, p  `r m2.neg.p`, \(\beta\)=`r m2.neg.Bt`)*, but not positive emotional resonance *(B=`r m2.poz.B`, t=`r m2.poz.t`, p  `r m2.poz.p`, \(\beta\)=`r m2.poz.Bt`)*, and compared by Twitter, engagement rates increased statistically significant on Facebook *(B=`r m2.Fcb.B`, t=`r m2.Fcb.t`, p  `r m2.Fcb.p`, \(\beta\)=`r m2.Fcb.Bt`)*, Instagram *(B=`r m2.Isg.B`, t=`r m2.Isg.t`, p  `r m2.Isg.p`, \(\beta\)=`r m2.Isg.Bt`)* and Youtube *(B=`r m2.Ytb.B`, t=`r m2.Ytb.t`, p  `r m2.Ytb.p`, \(\beta\)=`r m2.Ytb.Bt`)*.
+
+Finally, the hypothesis *H~3~*: *The effect of emotional resonance on public engagement is moderated by the social media platform utilized* was also plausible (F(`r m3.F.df1`, `r m3.F.df2`)=`r m3.F`, p `r m3.F.p`), the model with interaction terms explaining `r m3.r2.p`% of engagement rate's variance (R^2^=`r m3.r2`, RSR=`r m3.RSE`) and had a statistically significant better prediction power than the second model (F(`r mod.com.df1`, `r mod.com.df2`)=`r mod.com.F`, p `r mod.com.p`).
+
+The main effect of negative emotional resonance was statistically significant *(B=`r m3.neg.B`, t=`r m3.neg.t`, p  `r m3.neg.p`, \(\beta\)=`r m3.neg.Bt`)*, but not the main effect of positive emotional resonance *(B=`r m3.poz.B`, t=`r m3.poz.t`, p  `r m3.poz.p`, \(\beta\)=`r m3.poz.Bt`)*, and both were moderated by social network.
+Furthermore, compared to Twitter influence, Facebook *(B=`r m3.Fbk.B`, t=`r m3.Fbk.t`, p  `r m3.Fbk.p`, \(\beta\)=`r m3.Fbk.Bt`)* and Youtube *(B=`r m3.Yut.B`, t=`r m3.Yut.t`, p  `r m3.Yut.p`, \(\beta\)=`r m3.Yut.Bt`)* were statistically significant positively associated with engagement rate, but not Instragram *(B=`r m3.Ins.B`, t=`r m3.Ins.t`, p  `r m3.Ins.p`, \(\beta\)=`r m3.Ins.Bt`)*.
+
+```{r, moderation-1, out.width = '510px', fig.align='center', fig.cap='Interaction effect between social network and negative emotional resonance on engagement rate', warning=FALSE}
+  Int.Plot.1
+```
+
+The positive association between negative emotional resonance and engagement rate *(B=`r m3.neg.B`, t=`r m3.neg.t`, p  `r m3.neg.p`, \(\beta\)=`r m3.neg.Bt`)* was moderated statistically significant and negatively by Youtube *(B=`r m3.NegYut.B`, t=`r m3.NegYut.t`, p  `r m3.NegYut.p`, \(\beta\)=`r m3.NegYut.Bt`)* and Facebook *(B=`r m3.NegFbk.B`, t=`r m3.NegFbk.t`, p  `r m3.NegFbk.p`, \(\beta\)=`r m3.NegFbk.Bt`)*, messages with negative emotional resonance posted on these social platforms reducing statistically significant the initial positive association.
+No moderation effect of Instagram was identified on association between negative emotional resonance and engagement rate *(B=`r m3.NegIns.B`, t=`r m3.NegIns.t`, p  `r m3.NegIns.p`, \(\beta\)=`r m3.NegIns.Bt`)* (see Fig.
+\@ref(fig:moderation-1))
+
+\center _Please Insert Fig. \@ref(fig:moderation-1) around here_ \justify
+
+```{r, moderation-2, out.width = '510px', fig.align='center', fig.cap='Interaction effect between social network and positive emotional resonance on engagement rate', warning=FALSE}
+  Int.Plot.2
+```
+
+Between positive emotional resonance and engagement rate was no statistically significant association, *(B=`r m3.poz.B`, t=`r m3.poz.t`, p  `r m3.poz.p`, \(\beta\)=`r m3.poz.Bt`)*, but our results showed a positive and statistically significant interaction effect with Instagram *(B=`r m3.PozIns.B`, t=`r m3.PozIns.t`, p  `r m3.PozIns.p`, \(\beta\)=`r m3.PozIns.Bt`)* and Youtube *(B=`r m3.PozYut.B`, t=`r m3.PozYut.t`, p  `r m3.PozYut.p`, \(\beta\)=`r m3.PozYut.Bt`)* (see Fig.
+\@ref(fig:moderation-2))
+
+\center _Please Insert Fig. \@ref(fig:moderation-2) around here_ \justify
+
+Compared to Twetter posts, if the messages with positive emotional resonance were posted on Instagram or Youtube, the engagement rate increased statistically significant and the effect was most powerfull on Instagram than on Youtube.
+No interaction effect was observed on Facebook related on positive emotional resonance *(B=`r m3.PozFbk.B`, t=`r m3.PozFbk.t`, p  `r m3.PozFbk.p`, \(\beta\)=`r m3.PozFbk.Bt`)*
 

### 2023-06-12 03 - Regressions.R

@@ -6,11 +6,11 @@ if(!require(lm.beta)) install.packages("lm.beta")
 if(!require(relaimpo)) install.packages("relaimpo")
 if(!require(ggpubr)) install.packages("ggpubr")
 if(!require(nortest)) install.packages("nortest")
+if(!require(interactions)) install.packages("interactions")
+if(!require(misty)) install.packages("misty")
 
 library(dplyr); library(caret); library(rstatix); library(ggpubr); library(lm.beta)
-library(relaimpo); library(nortest)
-
-# Function for p-values management ####
+library(relaimpo); library(nortest); library(interactions)
 p <- function(x, digits = 3){
   if (x < 10^-digits) return(paste('<', 10^-digits))
   paste('=', round(x, 3))}
@@ -18,7 +18,7 @@ p <- function(x, digits = 3){
 # Loading datasets ####
 load(file = "Pure Sentiment.RData"); head(ds.pur)
 
-# Preparing datasets
+# Preparing datasets ####
 set.seed(453447)
 selection <- ds.pur$ER %>% createDataPartition(p = 0.8, list = FALSE)
 ds.estim  <- ds.pur[selection, ]; ds.asses <- ds.pur[-selection, ]; rm(selection)
@@ -75,7 +75,7 @@ m1.poz.B <- formatC(mod.std$coefficients[3, 1], format = "f", digits = 5)
 m1.poz.t <- round(mod.std$coefficients[3, 4], 2)
 m1.poz.p <- p(mod.std$coefficients[3, 5], digits = 3)
 m1.poz.Bt <- round(mod.std$coefficients[3, 2], 3)
-## Relative predictors importance ####
+## Relative predictors importance
 m1.relimp <- calc.relimp(mod.1, type = c("lmg"), rela = T); m1.relimp
 m1.poz.lmg <- round(as.numeric(m1.relimp@lmg[2]) * 100, 2)
 m1.neg.lmg <- round(as.numeric(m1.relimp@lmg[1]) * 100, 2)
@@ -90,7 +90,7 @@ m2.F.df1 <- round(mod.std[["fstatistic"]][["numdf"]], 2)
 m2.F.df2 <- round(mod.std[["fstatistic"]][["dendf"]], 2)
[…]

### 2023-06-12 Article.Rmd
Packages citation updated. Proofread ready

@@
 keywords          : "social media, public institutions, emotional resonance, public engagement, platform-specific strategies, digital governance"
-wordcount         : "X"
+wordcount         : "4067 words in text body 1034 words in reference section"
 bibliography      : ["r-references.bib", "references.bib"]
@@
   library(sasLM);library(rstatix); library(naniar); library(lubridate); library(flextable)
+  library(caret); library(ggpubr); library(lm.beta); library(relaimpo); library(nortest)
+  library(interactions); library(misty); library(tm); library(SentimentAnalysis); library(ggplot2)
 

### 2023-06-12 00 - Data processing.R

@@ -1,25 +1,8 @@
 # Installing and loading libraries
 if (!require(readxl)) install.packages("readxl")
 if (!require(dplyr)) install.packages("dplyr")
-# if (!require(writexl)) install.packages("writexl")
-# if (!require(tidytext)) install.packages("tidytext")
-# if (!require(tidyverse)) install.packages("tidyverse")
-# if (!require(tm)) install.packages("tm")
-# if (!require(textdata)) install.packages("textdata")
-# if (!require(textdata)) install.packages("textdata")
-# if (!require(SnowballC)) install.packages("SnowballC")
-# if (!require(wordcloud)) install.packages("wordcloud")
-# if (!require(RColorBrewer)) install.packages("RColorBrewer")
-# if (!require(syuzhet)) install.packages("syuzhet")
-# if (!require(ggplot2)) install.packages("ggplot2")
-# if (!require(lubridate)) install.packages("lubridate")
-# if (!require(scales)) install.packages("scales")
-
 
 library(readxl); library(dplyr)
-# library(writexl); library(tidytext); library(tidyverse); library(tm); library(textdata)
-# library(SnowballC); library(wordcloud); library(RColorBrewer); library(syuzhet); library(ggplot2 )
-# library(lubridate); library(scales); library(SentimentAnalysis)
 
 # Data import
 facebook <- read_xlsx("facebook.xlsx"); facebook$Page <- "Facebook"; facebook <- select(facebook, Page, Message, Type, Date, Reactions, Likes, Comments, Shares, Fans)

### 2023-06-12 Article.Rmd
1

@@
 
-Compared to Twetter posts, if the messages with positive emotional resonance were posted on Instagram or Youtube, the engagement rate increased statistically significant and the effect was most powerfull on Instagram than on Youtube.
+Compared to Twitter posts, if the messages with positive emotional resonance were posted on Instagram or Youtube, the engagement rate increased statistically significant and the effect was most powerfull on Instagram than on Youtube.
 No interaction effect was observed on Facebook related on positive emotional resonance *(B=`r m3.PozFbk.B`, t=`r m3.PozFbk.t`, p  `r m3.PozFbk.p`, \(\beta\)=`r m3.PozFbk.Bt`)*

### 2023-06-13 Article.Rmd
refacut abstract + discussions

@@
 abstract: |
-  This study investigates the role of emotional resonance in social media communications from the European Commission (EC) and its impact on public engagement across different platforms (Facebook, Instagram, Twitter, and YouTube).
-Our results indicate that messages with emotional resonance significantly boost public engagement levels, with the effects varying based on the specific platform.
-We further reveal a notable influence of both positive and negative emotional resonance on engagement, with the latter exerting a stronger impact.
-This research expands our understanding of engagement dynamics on different platforms, stressing the importance of tailored platform-specific strategies.
-The findings underscore the crucial role of social media in enhancing public involvement in policy dialogue and emphasize the need for public institutions to incorporate emotional resonance into their communication strategies, accounting for unique platform characteristics.
-These insights provide a foundation for future discussions and research into optimizing communication strategies within a multi-platform environment, which will shape the future of digital governance and public policymaking.
+ This study investigates the role of emotional resonance in social media communications from the European Commission (EC) and its impact on public participation across various platforms including Facebook, Instagram, Twitter, and YouTube.
+Findings indicate that emotionally resonant communications significantly enhance public engagement, with variations depending on the specific platform.
+Both positive and negative emotional resonance significantly impact participation, with the latter having a more pronounced effect.
+Our research highlights the critical importance of platform-specific strategies and the incorporation of emotional resonance in public communications to foster participation in policy dialogues.
+An analysis of the engagement rates and sentiment across platforms reveals unique tonal variations in the EC's discourse.
+The effect of emotional resonance on public engagement is also found to be moderated by the choice of social media platform, with certain platforms more significantly moderating the relationship between emotional resonance and engagement than others.
+This study lays the groundwork for refining communication strategies within a multi-platform digital governance environment.
+
 keywords          : "social media, public institutions, emotional resonance, public engagement, platform-specific strategies, digital governance"
@@
 # Discussion
-This investigation commenced with the aim of assessing the impact of citizen engagement on the European Commission's social media platforms by specifically evaluating the influence of emotionally resonant communications on public engagement levels.
-The discussion here explores the findings derived from the study and their implications, juxtaposing them against the extant body of research on social media engagement, public institutional communication, and the role of emotional resonance in these facets.
+The present investigation embarked on a quest to explore public engagement across various social media platforms utilized by the European Commission, with an emphasis on the impact of emotional resonance within content.
+The role of social media in public institutions' communication strategies is pivotal [@Smith2015], necessitating a deep understanding of engagement dynamics.
 
-The first hypothesis (H1) was predicated on the notion that communications with emotional resonance would yield higher public engagement levels.
-The research findings provided empirical support to this hypothesis, demonstrating a significant association between emotionally resonant communications and amplified levels of public engagement.
-This echoes previous scholarly work emphasizing the role of emotional appeal in enhancing audience engagement on social media platforms (Dolan et al., 2016; Smith & Gallicano, 2015).
-However, our research contributes a new dimension by bringing these aspects into the realm of public institutions, specifically the European Commission.
+The data supports our first hypothesis (H1), suggesting that communications rich in emotional resonance, whether of positive or negative valence, are correlated with enhanced public engagement.
+However, the ability of emotional resonance to elucidate engagement levels is negligible (0.16%).
+This corroborates the complex nature of engagement behaviours expounded in scholarly literature [@Dolan2016; @Dragseth2020; @Mirbagheri2019] and points towards the necessity for further examination of supplementary factors influencing public engagement.
 
-Public institutions often struggle with perceived remoteness and disconnection from citizens.
-However, the advent of social media offers a new avenue for these institutions to reach out to their citizenry, thereby allowing them to foster greater trust and engagement.
-Our findings confirm that the integration of emotional resonance within these online communications could significantly enhance this engagement process, fostering a more meaningful and interactive dialogue between the institutions and citizens.
+Our second hypothesis (H2) posited the influence of the social media platform choice on the effect of emotional resonance on public engagement.
+The empirical evidence supports this, suggesting that different platforms may cater to varied user expectations and norms.
+These findings align with prior research that demonstrated platform-specific fluctuations in engagement patterns [@Voorveld2018], underscoring the need for the European Commission to acknowledge heterogeneous engagement patterns and tailor their communications accordingly.
 
-Our findings align with the theoretical underpinnings of the uses and gratifications theory, emphasizing that emotional resonance serves as a primary motivation for users to engage with social media content.
-Consequently, public institutions should incorporate emotionally resonant messages into their social media communications to meet these user motivations, thus promoting higher engagement levels.
-This reflects the findings of Dolan et al.
-(2016), who identified emotional resonance as a key motivator in user engagement behavior.
+The third hypothesis (H3) asserted that the social media platform would moderate the impact of emotional resonance on public engagement.
+Our data confirmed this assumption, revealing a statistically significant moderating effect.
+This suggests that platforms may shape the way the public interacts with emotionally resonant messages, emphasizing the importance of customizing such communications to align with each platform's norms.
 
-The second hypothesis (H2) postulated that the social media platform could exert an influence on the emotional resonance in public engagement.
-The findings of the study substantiated this claim, revealing that the type of social media platform indeed moderates the impact of emotional resonance on public engagement.
-This variability across platforms underscores the need for a more nuanced, platform-specific approach to communication strategies.
+Despite these findings, the study is not without limitations.
+The low R^2 values in our regression models indicate that other unexamined variables might have significant effects on public engagement levels.
+Future research should persist in exploring these potential factors, acknowledging the complex and multifaceted nature of engagement behaviours.
 
-Such an approach resonates with the findings of @Voorveld2018 who noted the differential roles of different social media platforms in user engagement.
-Public institutions, therefore, need to be mindful of these variations, ensuring that their communication strategies are tailored to the specific features, functionalities, and user behaviors of each platform to maximize the effectiveness of their emotionally resonant communications.
+Additionally, the scope of our research was limited to the European Commission's use of four major social media platforms.
+Further studies could explore other platforms or public institutions to see if the observed patterns hold.
+Also, while we focused on emotional resonance, other aspects of communication such as tone, complexity, and framing could be investigated in future research.
 
-Our third hypothesis (H3) proposed that the social media platform could moderate the effect of emotional resonance on public engagement.
-This hypothesis was also validated by the study, underscoring the pivotal role that the choice of the social media platform plays in shaping public engagement levels.
-Each platform presents unique attributes and user behaviors, influencing the extent to which emotional resonance can stimulate public engagement.
-
-This finding also converges with the research conducted by @Voorveld2018, which asserted the differentiating impact of platform type on social media engagement.
-Hence, the insights derived from our study reinforce the need for public institutions to strategically consider their choice of social media platform, factoring in the distinctive characteristics of each platform and their corresponding audience base to optimize their emotionally resonant communications.
-
-A particularly interesting revelation was the relative impact of positive and negative emotional resonance on engagement levels.
-Both types of emotional resonance were found to amplify engagement levels, yet negative emotional resonance appeared to exert a stronger influence.
-This suggests that audiences may be more inclined to engage with messages that evoke negative emotions.
-Public institutions must carefully navigate this complex terrain, ensuring that their communications strike a delicate balance between positive and negative emotional resonance, taking into consideration the potential risks and rewards of each approach.
-
-In sum, this study provides a wealth of empirical evidence to support the significance of emotional resonance in amplifying citizen engagement on the social media platforms of public institutions.
-It is a clarion call for public organizations to strategically incorporate emotional resonance into their communications, thereby leveraging this engagement driver to foster a more interactive, engaging dialogue with their audiences.
-Further, it highlights the pivotal role of platform choice, emphasizing the need to take into account the unique attributes and audiences of each platform in formulating and executing effective communication strategies.
-
-However, despite its contributions, this study is not without its limitations.
-Future research should delve deeper into the intricate relationship between emotional resonance and public engagement, examining potential moderating factors such as the type of communication, audience demographics, or the cultural context.
-Additionally, further studies could evaluate the differential impact of positive and negative emotional resonance, providing a more nuanced understanding of how these contrasting types of emotional appeal influence public engagement.
-The role of individual social media platforms and their unique features in shaping emotional resonance could also be explored in more detail, providing insights into how public institutions can optimize their platform-specific strategies.
-
-This research offers a critical springboard for public institutions to understand and leverage emotional resonance in their social media communications, thereby unlocking new opportunities for more effective and engaging citizen interactions.
-As public institutions continue to navigate the digital landscape, they must take these findings into account, recognizing the crucial role of emotional resonance in social media communications as well as the importance of adopting a platform-specific approach.
-The benefits of doing so will not only enhance public engagement but also foster a stronger, more trustful relationship between public institutions and their audiences.
+In conclusion, this study underscores the significance of emotional resonance and platform-specific norms in driving public engagement.
+It suggests that forming an emotional connection with the audience through posts could amplify engagement levels.
+By understanding these dynamics, public institutions like the European Commission can refine their social media strategies, enhance citizen engagement, and bolster the efficacy of their public communication.
+Despite the limitations, the study provides a valuable starting point for future research into the multifaceted world of social media engagement.
 

### 2023-06-13 Article.Rmd
Schimba la linia 246

@@
 # Discussion
-The present investigation embarked on a quest to explore public engagement across various social media platforms utilized by the European Commission, with an emphasis on the impact of emotional resonance within content.
+This investigation embarked on a quest to explore public engagement across various social media platforms utilized by the European Commission, with an emphasis on the impact of emotional resonance within content.
 The role of social media in public institutions' communication strategies is pivotal [@Smith2015], necessitating a deep understanding of engagement dynamics.
 
-The data supports our first hypothesis (H1), suggesting that communications rich in emotional resonance, whether of positive or negative valence, are correlated with enhanced public engagement.
-However, the ability of emotional resonance to elucidate engagement levels is negligible (0.16%).
-This corroborates the complex nature of engagement behaviours expounded in scholarly literature [@Dolan2016; @Dragseth2020; @Mirbagheri2019] and points towards the necessity for further examination of supplementary factors influencing public engagement.
+The data supports our first hypothesis (H1), suggesting that communications rich in emotional resonance, whether of positive or negative valence, are associated with enhanced public engagement.
+However, the ability of emotional resonance to explain engagement levels is negligible (0.16%).
+This corroborates the complex nature of engagement behaviors expounded in scholarly literature [@Dolan2016; @Dragseth2020; @Mirbagheri2019] and points towards the necessity for further examination of supplementary factors influencing public engagement.
 
@@
 The third hypothesis (H3) asserted that the social media platform would moderate the impact of emotional resonance on public engagement.
-Our data confirmed this assumption, revealing a statistically significant moderating effect.
+Our data sustained this assumption, revealing a statistically significant moderating effect.
 This suggests that platforms may shape the way the public interacts with emotionally resonant messages, emphasizing the importance of customizing such communications to align with each platform's norms.
@@
 The low R^2 values in our regression models indicate that other unexamined variables might have significant effects on public engagement levels.
-Future research should persist in exploring these potential factors, acknowledging the complex and multifaceted nature of engagement behaviours.
+Future research should persist in exploring these potential factors, acknowledging the complex and multifaceted nature of engagement behaviors.
 
@@
 
-In conclusion, this study underscores the significance of emotional resonance and platform-specific norms in driving public engagement.
+To conclude, this study underscores the significance of emotional resonance and platform-specific norms in driving public engagement.
 It suggests that forming an emotional connection with the audience through posts could amplify engagement levels.

### 2023-06-13 Article.Rmd
1

--- 2023-06-13 Article.Rmd
@@
 
-Despite these findings, the study is not without limitations.
-The low R^2 values in our regression models indicate that other unexamined variables might have significant effects on public engagement levels.
-Future research should persist in exploring these potential factors, acknowledging the complex and multifaceted nature of engagement behaviours.
-
 Additionally, the scope of our research was limited to the European Commission's use of four major social media platforms.

### 2023-06-13 Article.Rmd
1

@@
 
+This research has limitations due to the use of secondary data obtained from platforms, suggesting future studies could benefit from primary data collection.
+Moreover, this study did not associate Engagement Rate (ER) with significant concurrent events, potentially overlooking the impact of emotional reactions based on these events.
+Future studies could explore these associations to understand emotional impacts better, thus extending the existing knowledge in the field.
+
 Additionally, the scope of our research was limited to the European Commission's use of four major social media platforms.

### 2023-06-13 Article.Rmd
1

@@
 ---
-title             : "From Likes to Change: Assessing the Impact of Citizen Engagement on the European Commission's Social Media Platforms"
-shorttitle        : "Impact of Citizen Engagement on the European Commission's Social Media Platforms"
+title: 'From Likes to Change: Assessing the Impact of Citizen Engagement on the European
+  Commission''s Social Media Platforms'
 author:
-  - name          : "Tanase Tasențe"
-    affiliation   : "1"
-    corresponding : yes    # Define only one corresponding author
-    address       : "Postal address"
-    email         : "tanase.tasente@365.univ-ovidius.ro"
-    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
-      - "Equal contribution"
-      - "Conceptualization"
-      - "Data curation"
-      - "Investigation"
-      - "Formal analysis"
-      - "Resources"
-      - "Software"
-      - "Visualization"
+- name: Tanase Tasențe
+  affiliation: '1'
+  corresponding: yes
+  address: Postal address
+  email: "tanase.tasente@365.univ-ovidius.ro"
+  role:
+  - Equal contribution
+  - Conceptualization
+  - Data curation
+  - Investigation
+  - Formal analysis
+  - Resources
+  - Software
+  - Visualization
   - "Writing - Original Draft Preparation"
   - "Writing - Review & Editing"
-  - name          : "Cristian Opariuc-Dan"
-    affiliation   : "1,2"
+- name: "Cristian Opariuc-Dan"
+  affiliation: '1,2'
   role:
-      - "Equal contribution"
+  - Equal contribution
   - "Writing - Original Draft Preparation"
   - "Writing - Review & Editing"
-      - "Data curation"
-      - "Formal analysis"
-      - "Resources"
-      - "Software"
-      - "Visualization"
-  - name          : "Cristina Dana Popescu"
-    affiliation   : "1"
+  - Data curation
+  - Formal analysis
+  - Resources
+  - Software
+  - Visualization
+- name: Cristina Dana Popescu
+  affiliation: '1'
   role:
@@
   - "Writing - Review & Editing"
-      - "Professional proofreading"
-affiliation:
-  - id            : "1"
-    institution   : "Ovidius University of Constanța, Romania"
-  - id            : "2"
-    institution   : "University of Bucharest, Romania"
+  - Professional proofreading
+shorttitle: Impact of Citizen Engagement on the European Commission's Social Media
+  Platforms
+output:
+  html_document:
+    df_print: paged
+  word_document: papaja::apa6_docx
+  pdf_document: papaja::apa6_pdf
 authornote: |
   Department of Administrative and Social Sciences
-abstract: |
- This study investigates the role of emotional resonance in social media communications from the European Commission (EC) and its impact on public participation across various platforms including Facebook, Instagram, Twitter, and YouTube.
-Findings indicate that emotionally resonant communications significantly enhance public engagement, with variations depending on the specific platform.
-Both positive and negative emotional resonance significantly impact participation, with the latter having a more pronounced effect.
-Our research highlights the critical importance of platform-specific strategies and the incorporation of emotional resonance in public communications to foster participation in policy dialogues.
-An analysis of the engagement rates and sentiment across platforms reveals unique tonal variations in the EC's discourse.
-The effect of emotional resonance on public engagement is also found to be moderated by the choice of social media platform, with certain platforms more significantly moderating the relationship between emotional resonance and engagement than others.
-This study lays the groundwork for refining communication strategies within a multi-platform digital governance environment.
-
-keywords          : "social media, public institutions, emotional resonance, public engagement, platform-specific strategies, digital governance"
-wordcount         : "4067 words in text body 1034 words in reference section"
-bibliography      : ["r-references.bib", "references.bib"]
-floatsintext      : no
-linenumbers       : yes
-draft             : no
-mask              : no
-figurelist        : no
-tablelist         : no
-footnotelist      : no
-documentclass     : "apa7"
-classoption       : "man"
-csl               : apa.csl
-output            :
-  pdf_document    : papaja::apa6_pdf
-  word_document   : papaja::apa6_docx
-header-includes:
-  - \usepackage{ragged2e}
+abstract: "This study investigates the role of emotional resonance in social media
+  communications from the European Commission (EC) and its impact on public participation
+  across various platforms including Facebook, Instagram, Twitter, and YouTube. Findings
+  indicate that emotionally resonant communications significantly enhance public engagement,
+  with variations depending on the specific platform. Both positive and negative emotional
+  resonance significantly impact participation, with the latter having a more pronounced
+  effect. Our research highlights the critical importance of platform-specific strategies
+  and the incorporation of emotional resonance in public communications to foster
+  participation in policy dialogues. An analysis of the engagement rates and sentiment
+  across platforms reveals unique tonal variations in the EC's discourse. The effect
+  of emotional resonance on public engagement is also found to be moderated by the
+  choice of social media platform, with certain platforms more significantly moderating
+  the relationship between emotional resonance and engagement than others. This study
+  lays the groundwork for refining communication strategies within a multi-platform
+  digital governance environment.\n"
+keywords: "social media, public institutions, emotional resonance, public engagement,
+  platform-specific strategies, digital governance"
+wordcount: 4067 words in text body 1034 words in reference section
+bibliography:
+- "r-references.bib"
+- references.bib
+floatsintext: no
+linenumbers: yes
+draft: no
+mask: no
+figurelist: no
+tablelist: no
+footnotelist: no
+documentclass: apa7
+classoption: man
+csl: apa.csl
+affiliation:
+- id: '1'
+  institution: Ovidius University of Constanța, Romania
+- id: '2'
+  institution: University of Bucharest, Romania
+header-includes: \usepackage{ragged2e}
 ---

### 2023-06-13 Article.Rmd
2

@@
 output:
+  pdf_document: papaja::apa6_pdf
+  word_document: papaja::apa6_docx
   html_document:
     df_print: paged
-  word_document: papaja::apa6_docx
-  pdf_document: papaja::apa6_pdf
 authornote: |
@@
 # Discussion
-The present investigation embarked on a quest to explore public engagement across various social media platforms utilized by the European Commission, with an emphasis on the impact of emotional resonance within content.
-The role of social media in public institutions' communication strategies is pivotal [@Smith2015], necessitating a deep understanding of engagement dynamics.
+The current study embarked on an investigative journey to examine public engagement across a range of social media platforms utilized by the European Commission, laying specific emphasis on the impact of emotional resonance within disseminated content.
+The vital role of social media in communication strategies of public institutions has been widely recognized [@Smith2015], accentuating the necessity for an in-depth comprehension of the dynamics of engagement.
 
-The data supports our first hypothesis (H1), suggesting that communications rich in emotional resonance, whether of positive or negative valence, are correlated with enhanced public engagement.
-However, the ability of emotional resonance to elucidate engagement levels is negligible (0.16%).
-This corroborates the complex nature of engagement behaviours expounded in scholarly literature [@Dolan2016; @Dragseth2020; @Mirbagheri2019] and points towards the necessity for further examination of supplementary factors influencing public engagement.
+Our collected data validates our primary hypothesis (H1), implying that communications imbued with emotional resonance, regardless of its positive or negative polarity, are associated with augmented public engagement.
+Nevertheless, the capacity of emotional resonance to illuminate engagement levels remains marginal (0.16%).
+This finding is consistent with the complex nature of engagement behaviours outlined in existing academic discourse [@Dolan2016; @Dragseth2020; @Mirbagheri2019], thereby underscoring the need for further scrutiny of additional factors influencing public engagement.
 
-Our second hypothesis (H2) posited the influence of the social media platform choice on the effect of emotional resonance on public engagement.
-The empirical evidence supports this, suggesting that different platforms may cater to varied user expectations and norms.
-These findings align with prior research that demonstrated platform-specific fluctuations in engagement patterns [@Voorveld2018], underscoring the need for the European Commission to acknowledge heterogeneous engagement patterns and tailor their communications accordingly.
+Our secondary hypothesis (H2) proposed that the choice of the social media platform would significantly influence the effect of emotional resonance on public engagement.
+The empirical evidence corroborates this assertion, indicating that different platforms potentially cater to diverse user expectations and conventions.
+This alignment with prior research revealing platform-specific variations in engagement patterns [@Voorveld2018] underscores the necessity for the European Commission to recognize and adapt to these heterogeneous engagement patterns when designing their communication strategies.
 
-The third hypothesis (H3) asserted that the social media platform would moderate the impact of emotional resonance on public engagement.
-Our data confirmed this assumption, revealing a statistically significant moderating effect.
-This suggests that platforms may shape the way the public interacts with emotionally resonant messages, emphasizing the importance of customizing such communications to align with each platform's norms.
+The tertiary hypothesis (H3) posited that the chosen social media platform would moderate the impact of emotional resonance on public engagement.
+The acquired data affirmed this premise, demonstrating a statistically significant moderating effect.
+This indicates that the characteristics of individual platforms may shape the public’s interaction with emotionally resonant messages, highlighting the need to tailor such communications to align with the norms specific to each platform.
 
-This research has limitations due to the use of secondary data obtained from platforms, suggesting future studies could benefit from primary data collection.
-Moreover, this study did not associate Engagement Rate (ER) with significant concurrent events, potentially overlooking the impact of emotional reactions based on these events.
-Future studies could explore these associations to understand emotional impacts better, thus extending the existing knowledge in the field.
+This research is constrained by its reliance on secondary data obtained from platforms, suggesting that future studies could potentially reap benefits from primary data collection methodologies.
+Furthermore, this study did not associate Engagement Rate (ER) with significant simultaneous events, potentially overlooking the effect of emotional reactions provoked by these events.
+Future investigations could probe these associations, thereby enhancing our understanding of emotional impacts and expanding the existing body of knowledge in this domain.
 
-Additionally, the scope of our research was limited to the European Commission's use of four major social media platforms.
-Further studies could explore other platforms or public institutions to see if the observed patterns hold.
-Also, while we focused on emotional resonance, other aspects of communication such as tone, complexity, and framing could be investigated in future research.
+Additionally, the scope of this research was confined to the European Commission's use of four primary social media platforms.
+Future inquiries could potentially explore other platforms or public institutions to determine the universality of the observed patterns.
+Furthermore, while our focus lay primarily on emotional resonance, future research could delve into other aspects of communication, such as tone, complexity, and framing.
 
-In conclusion, this study underscores the significance of emotional resonance and platform-specific norms in driving public engagement.
-It suggests that forming an emotional connection with the audience through posts could amplify engagement levels.
-By understanding these dynamics, public institutions like the European Commission can refine their social media strategies, enhance citizen engagement, and bolster the efficacy of their public communication.
-Despite the limitations, the study provides a valuable starting point for future research into the multifaceted world of social media engagement.
+To conclude, this study underscores the imperative role of both emotional resonance and platform-specific norms in propelling public engagement on social media.
+The ability to establish an emotional connection with the audience, made possible through well-conceived and executed posts, emerges as a powerful tool for amplifying engagement levels.
+Such engagement is not merely about expanding the reach or visibility of public institutions like the European Commission, but is a mechanism for fostering a dynamic and participatory relationship between these institutions and the citizens they serve.
+
+Understanding these dynamics enables public institutions to tailor their communication strategies more effectively.
+By acknowledging the varying norms and expectations tied to different social media platforms, institutions can ensure that their messages resonate more strongly with their intended audiences, ultimately enhancing the impact and penetration of these messages.
+The choice of platform is not incidental but plays a significant role in how emotional resonance influences engagement, urging public institutions to be thoughtful and strategic in their selection and use of these platforms.
+
+Moreover, by refining their social media strategies based on these findings, public institutions have the opportunity to foster greater citizen engagement.
+Higher engagement can lead to increased public awareness, enhanced understanding, and potentially even behavioural change - critical goals for public communication strategies.
+It can also help public institutions gain insight into public sentiment, thus providing valuable feedback that can be used to improve policies and services.
+
+In addition, the insights derived from this study can help public institutions increase the effectiveness of their public communication.
+By leveraging emotional resonance and considering platform-specific norms, these institutions can design messages that are more likely to engage citizens and generate a meaningful response.
+This has the potential to transform the landscape of public communication, making it a more interactive, responsive, and impactful domain.
+
+Despite its limitations, this study provides an invaluable point of departure for further research into the intricate world of social media engagement.
+It opens up avenues for exploring other influential factors and for deepening our understanding of the relationship between emotional resonance, platform norms, and public engagement.
+These insights could be crucial in helping public institutions navigate the complex dynamics of social media engagement, enhancing their ability to communicate effectively with the public, and ultimately, improving their service to society.
 

### 2023-06-13 Article.Rmd

@@
 
+This investigation embarked on a quest to explore public engagement across various social media platforms utilized by the European Commission, with an emphasis on the impact of emotional resonance within content.
+The role of social media in public institutions' communication strategies is pivotal [@Smith2015], necessitating a deep understanding of engagement dynamics.
+
+The data supports our first hypothesis (H1), suggesting that communications rich in emotional resonance, whether of positive or negative valence, are associated with enhanced public engagement.
+However, the ability of emotional resonance to explain engagement levels is negligible (0.16%).
+This corroborates the complex nature of engagement behaviors expounded in scholarly literature [@Dolan2016; @Dragseth2020; @Mirbagheri2019] and points towards the necessity for further examination of supplementary factors influencing public engagement.
+
 Our secondary hypothesis (H2) proposed that the choice of the social media platform would significantly influence the effect of emotional resonance on public engagement.
@@
 Future investigations could probe these associations, thereby enhancing our understanding of emotional impacts and expanding the existing body of knowledge in this domain.
+
+The third hypothesis (H3) asserted that the social media platform would moderate the impact of emotional resonance on public engagement.
+Our data sustained this assumption, revealing a statistically significant moderating effect.
+This suggests that platforms may shape the way the public interacts with emotionally resonant messages, emphasizing the importance of customizing such communications to align with each platform's norms.
+
+Despite these findings, the study is not without limitations.
+The low R^2 values in our regression models indicate that other unexamined variables might have significant effects on public engagement levels.
+Future research should persist in exploring these potential factors, acknowledging the complex and multifaceted nature of engagement behaviors.
 
@@
 
+To conclude, this study underscores the significance of emotional resonance and platform-specific norms in driving public engagement.
+It suggests that forming an emotional connection with the audience through posts could amplify engagement levels.
+By understanding these dynamics, public institutions like the European Commission can refine their social media strategies, enhance citizen engagement, and bolster the efficacy of their public communication.
+Despite the limitations, the study provides a valuable starting point for future research into the multifaceted world of social media engagement.
 \newpage

### 2023-06-14 Article.Rmd
Final paper

@@
 Despite these findings, the study is not without limitations.
-The low R^2 values in our regression models indicate that other unexamined variables might have significant effects on public engagement levels.
-Future research should persist in exploring these potential factors, acknowledging the complex and multifaceted nature of engagement behaviors.
-
-Additionally, the scope of this research was confined to the European Commission's use of four primary social media platforms.
+The scope of this research was confined to the European Commission's use of four primary social media platforms.
 Future inquiries could potentially explore other platforms or public institutions to determine the universality of the observed patterns.
 Furthermore, while our focus lay primarily on emotional resonance, future research could delve into other aspects of communication, such as tone, complexity, and framing.
+
+This research has also limitations due to the use of secondary data obtained from platforms, suggesting future studies could benefit from primary data collection.
+Additionally, this study did not associate Engagement Rate (ER) with significant concurrent events, potentially overlooking the impact of emotional reactions based on these events.
+Future studies could explore these associations to understand emotional impacts better, thus extending the existing knowledge in the field.
 

### 2023-06-14 Article.Rmd
Articol final modificat

@@
 ---
-title: 'From Likes to Change: Assessing the Impact of Citizen Engagement on the European
-  Commission''s Social Media Platforms'
-author:
-- name: Tanase Tasențe
-  affiliation: '1'
-  corresponding: yes
-  address: Postal address
-  email: "tanase.tasente@365.univ-ovidius.ro"
-  role:
-  - Equal contribution
-  - Conceptualization
-  - Data curation
-  - Investigation
-  - Formal analysis
-  - Resources
-  - Software
-  - Visualization
+title             : "From Likes to Change: Assessing the Impact of Citizen Engagement on the European Commission's Social Media Platforms"
+shorttitle: "Impact of Citizen Engagement on the European Commission's Social Media Platforms"
+author            :
+- name            : "Tanase Tasențe"
+  affiliation     : '1'
+  corresponding   : yes
+  address         : "Aleea Universității"
+  email           : "tanase.tasente@365.univ-ovidius.ro"
+  role            :
+    - "Equal contribution"
+    - "Conceptualization"
+    - "Data curation"
+    - "Investigation"
+    - "Formal analysis"
+    - "Resources"
+    - "Software"
+    - "Visualization"
     - "Writing - Original Draft Preparation"
     - "Writing - Review & Editing"
-- name: "Cristian Opariuc-Dan"
-  affiliation: '1,2'
-  role:
-  - Equal contribution
+- name            : "Cristian Opariuc-Dan"
+  affiliation     : '1,2'
+  role            :
+    - "Equal contribution"
     - "Writing - Original Draft Preparation"
     - "Writing - Review & Editing"
-  - Data curation
-  - Formal analysis
-  - Resources
-  - Software
-  - Visualization
-- name: Cristina Dana Popescu
-  affiliation: '1'
-  role:
+    - "Data curation"
+    - "Formal analysis"
+    - "Resources"
+    - "Software"
+    - "Visualization"
+- name            : "Cristina Dana Popescu"
+  affiliation     : '1'
+  role            :
     - "Writing - Original Draft Preparation"
     - "Writing - Review & Editing"
-  - Professional proofreading
-shorttitle: Impact of Citizen Engagement on the European Commission's Social Media
-  Platforms
-output:
-  pdf_document: papaja::apa6_pdf
-  word_document: papaja::apa6_docx
-  html_document:
-    df_print: paged
+    - "Professional proofreading"
+affiliation     :
+  - id          : '1'
+    institution : "Ovidius University of Constanța, Romania"
+  - id          : '2'
+    institution : "University of Bucharest, Romania"
 authornote: |
-  Department of Administrative and Social Sciences
-abstract: "This study investigates the role of emotional resonance in social media
-  communications from the European Commission (EC) and its impact on public participation
-  across various platforms including Facebook, Instagram, Twitter, and YouTube. Findings
-  indicate that emotionally resonant communications significantly enhance public engagement,
-  with variations depending on the specific platform. Both positive and negative emotional
-  resonance significantly impact participation, with the latter having a more pronounced
-  effect. Our research highlights the critical importance of platform-specific strategies
-  and the incorporation of emotional resonance in public communications to foster
-  participation in policy dialogues. An analysis of the engagement rates and sentiment
-  across platforms reveals unique tonal variations in the EC's discourse. The effect
-  of emotional resonance on public engagement is also found to be moderated by the
-  choice of social media platform, with certain platforms more significantly moderating
-  the relationship between emotional resonance and engagement than others. This study
-  lays the groundwork for refining communication strategies within a multi-platform
-  digital governance environment.\n"
-keywords: "social media, public institutions, emotional resonance, public engagement,
-  platform-specific strategies, digital governance"
-wordcount: 4067 words in text body 1034 words in reference section
-bibliography:
-- "r-references.bib"
-- references.bib
-floatsintext: no
-linenumbers: yes
-draft: no
-mask: no
-figurelist: no
-tablelist: no
-footnotelist: no
-documentclass: apa7
-classoption: man
-csl: apa.csl
-affiliation:
-- id: '1'
-  institution: Ovidius University of Constanța, Romania
-- id: '2'
-  institution: University of Bucharest, Romania
-header-includes: \usepackage{ragged2e}
+
+  Tanase Tasente (Orcid ID: https://orcid.org/0000-0002-3164-5894) is a lecturer and ERASMUS coordinator at the Faculty of Law and Administrative Sciences at Ovidius University in Constanta.
+He holds a bachelor's, master's, and doctoral degree in Communication Sciences and a master's degree in European Administration, Institutions, and Public Policies.
+With over 100 published scientific papers and 4 authored books on institutional communication through social media and public policy strategies, the author has made significant contributions to the academic community.
+Additionally, he is the director of two international public relations companies, Plus Communication and International Communication & PR, where they have overseen marketing, advertising, and public relations campaigns for renowned multinational companies.
+His combination of academic and professional experience has equipped them with the necessary skills and knowledge to excel in various fields of communication and administration.
+  Cristian Opariuc-Dan (Orcid ID: https://orcid.org/0000-0003-4079-0142) is a lecturer at the Faculty of Law and Administrative Sciences at Ovidius University in Constanta.
+He holds a Bachelor's degree in Psychology, a Master's degree in Administrative Sciences, and a PhD in Psychology.
+He serves as the coordinator of the Law and Public Administration programs (part-time education) at Ovidius University and is an associate professor in the Doctoral Schools of Psychology and Education Sciences at the University of Bucharest and "Al.
+I.
+Cuza" University in Iasi.
+With over 50 scientific articles published in specialized journals and as the author and co-author of 5 books in the field of statistics and data analysis, he has demonstrated his expertise in the academic field.
+abstract: |
+  This study investigates the role of emotional resonance in social media  communications from the European Commission (EC) and its impact on public participation across various platforms including Facebook, Instagram, Twitter, and YouTube.
+Findings  indicate that emotionally resonant communications significantly enhance public engagement, with variations depending on the specific platform.
+Both positive and negative emotional resonance significantly impact participation, with the latter having a more pronounced  effect.
+Our research highlights the critical importance of platform-specific strategies and the incorporation of emotional resonance in public communications to foster participation in policy dialogues.
+An analysis of the engagement rates and sentiment across platforms reveals unique tonal variations in the EC's discourse.
+The effect of emotional resonance on public engagement is also found to be moderated by the choice of social media platform, with certain platforms more significantly moderating the relationship between emotional resonance and engagement than others.
+This study lays the groundwork for refining communication strategies within a multi-platform   digital governance environment.
+
+keywords        : "social media, public institutions, emotional resonance, public engagement, platform-specific strategies, digital governance"
+wordcount       : "4275 words in text body 1034 words in reference section"
+bibliography    : ["r-references.bib", "references.bib"]
+floatsintext    : no
+linenumbers     : yes
+draft           : no
+mask            : no
+figurelist      : no
+tablelist       : no
+footnotelist    : no
+documentclass   : "apa7"
+classoption     : "man"
+csl             : apa.csl
+header-includes : \usepackage{ragged2e}
+output          :
+  pdf_document  : papaja::apa6_pdf
+  html_document :
+    df_print    : paged
+  word_document : papaja::apa6_docx
 ---
 
-```{r setup, include = FALSE}
+```{r setup, include = FALSE, echo=FALSE}
   library(papaja); library(knitr); library(readxl); library(dplyr); library(psych)
@@
   library(interactions); library(misty); library(tm); library(SentimentAnalysis); library(ggplot2)
-
   r_refs("r-references.bib")
@@
 
-```{r analysis-preferences}
+```{r analysis-preferences, echo=FALSE}
 # Seed for random number generation

### 2023-06-14 Article.Rmd
Cristina included as author

@@
 His combination of academic and professional experience has equipped them with the necessary skills and knowledge to excel in various fields of communication and administration.
+
     Cristian Opariuc-Dan (Orcid ID: https://orcid.org/0000-0003-4079-0142) is a lecturer at the Faculty of Law and Administrative Sciences at Ovidius University in Constanta.
@@
 With over 50 scientific articles published in specialized journals and as the author and co-author of 5 books in the field of statistics and data analysis, he has demonstrated his expertise in the academic field.
+
+    Cristina-Dana Popescu (Orcid ID: ) is a Lecturer at the Faculty of Letters, the Faculty of Law and Administrative Sciences and at the Faculty of Mathematics and Informatics at Ovidius University in Constanta.
+She holds a Bachelor’s degree in Philology at the University of Bucharest, the Faculty of Foreign Languages and Literatures, English and German Department, a Master's degree in Philosophy at the University “Al.
+I.
+Cuza”, Iaşi, Romania and a Ph.D.
+in Philology - British and American Literature, at the University “Al.
+I.
+Cuza”, Iaşi, Romania.
+She has been teaching English since 1999 being also a School Director for 12 years of a private High School in Constanta, she is an accomplished teacher with demonstrated ability to teach, motivate and direct students while maintaining high interest and achievement.
+She holds the Excellence Award within the Faculty of Letters, as the winner of the Performance in Education Competition at Ovidius University in Constanta.
+She also holds internationally recognized trainings in the field of psychology, being a licensed NLP Practitioner at the International Association for Neuro-Linguistic Programming and also a licensed of Silva Method, the Immersion Silva Life and Intuition System at Silva International Headquarters, Laredo, Texas, USA.
+She also holds the qualification of Trainer, COR Code 242401, certified by SC Training & Teaching Center, București.With over 30 scientific articles published in specialized journals at national and international conferences, author of ISI and BDI articles, participant both in CNCSIS grant teams and in University Projects as Expert in the Study Programs Pillars and Expert in Educational Material Development and also author of 3 books and co-author of 1 book in the field of literature and various specialized languages, she has demonstrated her expertise in the academic field.
+
 abstract: |

### 2023-06-17 Article.Rmd
Corrected article

@@
 
-    Cristina-Dana Popescu (Orcid ID: ) is a Lecturer at the Faculty of Letters, the Faculty of Law and Administrative Sciences and at the Faculty of Mathematics and Informatics at Ovidius University in Constanta.
+    Cristina-Dana Popescu (Orcid ID: https://orcid.org/0009-0009-5280-6608) is a Lecturer at the Faculty of Letters, the Faculty of Law and Administrative Sciences and at the Faculty of Mathematics and Informatics at Ovidius University in Constanta.
 She holds a Bachelor’s degree in Philology at the University of Bucharest, the Faculty of Foreign Languages and Literatures, English and German Department, a Master's degree in Philosophy at the University “Al.
@@
 abstract: |
-  This study investigates the role of emotional resonance in social media  communications from the European Commission (EC) and its impact on public participation across various platforms including Facebook, Instagram, Twitter, and YouTube.
-Findings  indicate that emotionally resonant communications significantly enhance public engagement, with variations depending on the specific platform.
-Both positive and negative emotional resonance significantly impact participation, with the latter having a more pronounced  effect.
-Our research highlights the critical importance of platform-specific strategies and the incorporation of emotional resonance in public communications to foster participation in policy dialogues.
-An analysis of the engagement rates and sentiment across platforms reveals unique tonal variations in the EC's discourse.
-The effect of emotional resonance on public engagement is also found to be moderated by the choice of social media platform, with certain platforms more significantly moderating the relationship between emotional resonance and engagement than others.
-This study lays the groundwork for refining communication strategies within a multi-platform   digital governance environment.
+  This research undertakes an examination of the function that emotional resonance plays in the social media communications disseminated by the European Commission (EC) and its subsequent influence on public involvement across a multitude of platforms such as Facebook, Instagram, Twitter, and YouTube.
+The findings of this research underscored that communications laden with emotional resonance considerably amplify public engagement, though the magnitude of this amplification is dependent on the individual platform.
+Furthermore, both positive and negative forms of emotional resonance exhibit a noteworthy influence on public participation.
+However, it has been observed that the impact of negative emotional resonance is more distinct and profound.
+Our research underscored the pivotal significance of employing strategies tailored to specific platforms and integrating emotional resonance into public communications as a means to stimulate participation in policy discourse.An analytical examination of both engagement rates and sentiment across various platforms unveils distinctive tonal nuances within the European Commission's discourse.
+
+The impact of emotional resonance on public engagement is noted to be contingent upon the specific social media platform employed, as certain platforms demonstrate a more pronounced moderating effect on the association between emotional resonance and engagement relative to others.
+This research provided the foundational framework for the enhancement of communicative strategies within a multi-platform digital governance environment comprising multiple platforms.
 
@@
 \justify
-In recent years, the rise of social media platforms has led to significant changes in the way institutions, including public organizations, communicate with their audiences.
-As a result, the importance of citizen engagement in the process of communication through social media has become increasingly recognized.
-This engagement involves not only a one-way flow of information from public institutions to citizens, but also an interactive dialogue between the two parties.
+In recent years, it has been observed that the ascendance of social media platforms precipitated noteworthy transformations in the communication strategies employed by institutions, inclusive of public organizations, to engage with their respective audiences.
+Consequently, the significance of citizen participation in the process of communication mediated through social media platforms, gained escalated acknowledgment.
+This participatory process transcends the conventional one-directional dissemination of information from public bodies to citizens.
+Rather, it encapsulates an interactive discourse, fostering a two-way dialogue between the engaged parties.
 
-The concept of engagement in social media has been studied extensively in recent years, with researchers exploring various aspects of this phenomenon.
-One such study, conducted by @Dolan2016, approached social media engagement behavior from a uses and gratifications perspective, focusing on the motivations and benefits that users derive from engaging with social media.
-Meanwhile, the study by @Dragseth2020 explored how social media can be used to build engagement among students in the context of political science education.
+The notion of engagement within the context of social media has been the subject of comprehensive scholarly investigation in recent years, with researchers delving into diverse facets of this phenomenon.
+One such study, conducted by @Dolan2016, scrutinized social media engagement behavior through the theoretical lens of the uses and gratifications paradigm, emphasizing the motivations and benefits users acquire from their interaction with social media platforms.
+Concurrently, an academic study undertaken by @Dragseth2020 probed the application of social media for fostering engagement among students, specifically within the field of political science education.
 
-Another important aspect of engagement in social media is the role it plays in activation campaigns aimed at consumers.
-@Mirbagheri2019 conceptualized and developed a scale to measure consumers' engagement with social media activation campaigns.
-Additionally, @Smith2015 analyzed public engagement with organizations through social media, highlighting the importance of two-way communication between public institutions and citizens.
+Another important aspect of engagement in social media pertains to its integral role in activation campaigns directed towards consumers.
+Mirbagheri et al.
+(2019) conceptualized and developed a scale to measure consumers' engagement with social media activation campaigns.
+Complementarily, a comprehensive analysis conducted by Smith et al.
+(2015) scrutinized public engagement with organizations via social media channels, highlighting the importance of two-way communication between public institutions and citizens.
+The distinctive role of platform type concerning engagement with social media and its corresponding advertising was examined meticulously by Voorveld et al.
+(2018).
+This research established that the magnitude of engagement diverges significantly across distinct social media platforms.
 
-The differentiating role of platform type in engagement with social media and social media advertising was explored by @Voorveld2018, who found that the level of engagement varies across different social media platforms.
-
-In addition to understanding the various aspects of engagement in social media, it is also important to recognize the significance of citizen engagement in the context of public institutions.
-Citizen engagement plays a critical role in ensuring transparency and accountability in public decision-making processes.
-Furthermore, engagement with citizens can lead to the development of more effective policies and programs that better serve the needs of the community.
-
+In addition to understanding the multifaceted dimensions of engagement within social media, it is of crucial importance to acknowledge the significance of citizen participation in the realm of public institutions.
+Citizen engagement is instrumental in guaranteeing transparency and accountability within public decision-making procedures.
+Furthermore, the proactive engagement of citizens can facilitate the formulation of efficacious policies and initiatives that are more adept at meeting the requirements of the broader community.
 Moreover, the importance of citizen engagement in the process of communication through social media cannot be overstated.
@@
 
-Citizen engagement through social media can also contribute to the empowerment of individuals and groups, giving them a voice in public decision-making processes and enabling them to hold public institutions accountable for their actions.
-This can help to build stronger, more resilient communities that are better equipped to respond to challenges and opportunities.
+Citizen participation via social media platforms can further contribute to the empowerment of individuals and collective entities, effectively granting them a decisive voice in public decision-making processes and providing a mechanism for holding public institutions accountable for their actions.
+This empowerment strategy can potentially engender the construction of robust, resilient communities possessing enhanced capacities to navigate both challenges and opportunities.
 
@@
 Understanding the various aspects of engagement in social media is critical for public institutions to effectively communicate with and serve the needs of their communities.
-By leveraging the power of social media to engage with citizens, public institutions can build trust, empower individuals and groups, and develop more effective policies and programs that better serve the needs of the community.
+By leveraging the power of social media to engage with citizens, public institutions can build trust, empower individuals and groups, and develop more effective policies and programs that effectively address the needs of the community.
 
 ## Literature review
-In studying the impact of citizen engagement on the European Commission's social media platforms, it is crucial to discern the key concepts that underpin this research.
-These concepts are engagement, social media platforms, and sentiment analysis, which form the backbone of many academic discourses that revolve around these themes.
+In examining the influence of citizen engagement on the social media platforms of the European Commission, it is imperative to discern and elucidate the fundamental concepts that underlie this research.
+The concepts in question encompass engagement, social media platforms, and sentiment analysis, constituting the foundational pillars of numerous scholarly discussions centered around these topics.
 
@@
 There is a myriad of ways in which citizens engage with politics on social media, from commenting on posts to sharing and liking content [@DeWilde2022].
-This interaction has been correlated with a spectrum of outcomes, such as influencing voting behavior [@marquartThisTimeNot2020] and attitudes towards vaccination [@mascheriniSocialMediaUse2022].
+This interaction has been correlated with a variety of outcomes, including voting behaviour [@marquartThisTimeNot2020] and vaccination attitudes.
+[@mascheriniSocialMediaUse2022].
 
 Simultaneously, social media platforms are becoming recognized as powerful tools for promoting and managing engagement.
-This dual role is exemplified in the case of the European Commission's activities in Romania [@Rus2021].
+This dual functionality is exemplified through the case study of the European Commission's endeavors in Romania.[@Rus2021].
 Recognizing the potential of these platforms to facilitate citizen engagement, EU institutions have taken steps to optimize their use, implementing various strategies [@Bene2022; @Kanol2021; @ozdemirBirdEyeView2022].
 
-In assessing the impact of citizen engagement on the EU's social media platforms, researchers employ an assortment of methods, one of which is sentiment analysis.
-This approach, which involves the systematic identification and categorization of the emotional tone behind words, aims to gauge public sentiment, attitudes, and emotions towards specific topics [@Wei2021].
+When evaluating the influence of citizen engagement on the social media platforms of the European Union, researchers utilize a variety of methodologies, including sentiment analysis.
+This approach entails a systematic process of identifying and categorizing the emotional undertones conveyed by textual expressions, with the objective of assessing public sentiment, attitudes, and emotions towards specific subjects.[@Wei2021].
 It has been applied in diverse contexts, such as analyzing the emotional distribution in EU smart city communication [@kowalikSocialMediaDistribution2021] and exploring public opinions on climate change policy [@Wei2021].
@@
 
-To sum up, understanding the impact of citizen engagement on the European Commission's social media platforms is a multifaceted issue.
-These platforms offer opportunities for meaningful citizen engagement and public communication, but their influence is dictated by a complex interplay of individual behavior, institutional strategy, societal trends, and technological developments.
-This complexity calls for a nuanced understanding of each constituent factor and their collective role in shaping the landscape of citizen engagement within the context of the European Commission's social media platforms.
-It is a call to researchers, policymakers, and practitioners to continuously explore this evolving realm to maximize the benefits of citizen engagement while mitigating its potential pitfalls.
+In conclusion, comprehending the impact of citizen engagement on the social media platforms of the European Commission encompasses a multifaceted matter.
+These platforms offer opportunities for substantive citizen engagement and public communication, yet their influence is contingent upon an intricate interplay of individual behavior, institutional strategy, societal trends, and technological advancements.
+This intricacy necessitates a nuanced comprehension of each constituent element and their collective contributions to shaping the landscape of citizen engagement within the context of the European Commission's social media platforms.
+Consequently, it calls upon researchers, policymakers, and practitioners to continuously explore this evolving domain in order to maximize the advantages of citizen engagement while mitigating potential drawbacks.
 
 # The present study
-Relying on the theoretical framework previously described, the present study aimed to investigate public engagement across various official European Commission social media platforms (Facebook, Instagram, Twitter, and YouTube).
-We also compared and contrasted the patterns, trends, and characteristics of online user interactions and responses across these platforms.
-Translating these aims into research questions (RQs), the present study investigated the following:
+Grounded in the aforementioned theoretical framework, the primary objective of the current research endeavour was to examine the extent of public engagement manifested on diverse official social media platforms employed by the European Commission.
+Specifically, this investigation encompassed platforms such as Facebook, Instagram, Twitter, and YouTube.
+Furthermore, the study sought to analyse and juxtapose the discernible patterns, trends, and distinctive attributes of online user interactions and responses observed within these platforms.
+In order to structure the inquiry, the research questions (RQs) that guided this investigation were as follows:
 
 - *RQ~1~*. How is the communication with emotional resonance associated with higher public engagement levels?
-- *RQ~2~*. Does social media platforms influences the emotional resonance on public engagement?
+- *RQ~2~*. Does social media platforms influence the emotional resonance on public engagement?
 - *RQ~3~*. Does social media platforms moderates the effect of emotional resonance on public engagement?
@@
 The novelty of our study lies in the fact that we have systematically compared and contrasted user engagement and emotional resonance across multiple social media platforms utilized by the European Commission.
-While previous research has generally focused on the impact of citizen engagement within a single social media platform, our study is unique in its comprehensive cross-platform analysis.
+While previous research has typically focused on the impact of citizen engagement within a single social media platform, our comprehensive cross-platform analysis makes this study unique.
 
-In this context, we have pursued an integrated approach to understanding how emotional resonance can influence public engagement levels across these platforms.
-Furthermore, we have explored the moderating effect of the social media platform itself on the impact of emotional resonance, a novel aspect that has not been fully addressed in previous research.
+Within this context, we have pursued an integrated approach to comprehending the potential influence of emotional resonance on the levels of public engagement observed within these platforms.
+Furthermore, our investigation encompasses an exploration of the moderating influence exerted by the underlying social media platform on the impact of emotional resonance, a novel aspect that has not been thoroughly explored in prior research.
 
-The innovative approach of this study allowed us to draw robust conclusions about the nuanced relationship between communication strategy, emotional resonance, platform choice, and public engagement.
-Our research has therefore not only provided key insights into the patterns of citizen engagement on European Commission's social media platforms, but also presented an advanced framework for understanding how such engagement can be effectively harnessed and maximized for public outreach and policymaking.
+The pioneering methodology implemented in this research allowed us to draw robust conclusions concerning the intricate interplay between communication strategy, emotional resonance, selection of platform, and public engagement.
+Consequently, our research has not only provided critical understanding of the modalities of citizen engagement on the social media platforms employed by the European Commission, but also proposed an advanced paradigm for comprehending how such engagement can be effectively harnessed and optimized for public outreach and policymaking.
 
@@
 The initial assumptions assessment was performed by descriptive univariate analysis, data screening for outliers, and missing cases analysis, to verify univariate normality.
-We further conducted a sentiment analysis, and, finally a linear moderated regression was used for hypothesis testing.
+An additional layer of sentiment analysis was carried out to provide a more comprehensive understanding.
+Lastly, a moderated linear regression model was used as the methodological tool for hypothesis testing.
 
@@
 ## Sentiment analysis
-A comprehensive sentiment analysis was conducted on data, both with (see Fig.
-\@ref(fig:boxplot-EXT) and Fig.
-\@ref(fig:sent-EXT)) and without extreme outliers (see Fig.
-\@ref(fig:boxplot-NEXT) and Fig.
-\@ref(fig:sent-NEXT)) suggesting distinctive tonal variations in the discourse employed by the European Commission across different social media platforms.
+An exhaustive sentiment analysis was conducted on the dataset, considering scenarios with and without extreme outliers, as illustrated in Figure @ref(fig:sent-NEXT)).
+This analysis suggested distinctive tonal variations employed by the European Commission across different social media platforms.
 
@@
 
-The main effect of negative emotional resonance was statistically significant *(B=`r m3.neg.B`, t=`r m3.neg.t`, p  `r m3.neg.p`, \(\beta\)=`r m3.neg.Bt`)*, but not the main effect of positive emotional resonance *(B=`r m3.poz.B`, t=`r m3.poz.t`, p  `r m3.poz.p`, \(\beta\)=`r m3.poz.Bt`)*, and both were moderated by social network.
-Furthermore, compared to Twitter influence, Facebook *(B=`r m3.Fbk.B`, t=`r m3.Fbk.t`, p  `r m3.Fbk.p`, \(\beta\)=`r m3.Fbk.Bt`)* and Youtube *(B=`r m3.Yut.B`, t=`r m3.Yut.t`, p  `r m3.Yut.p`, \(\beta\)=`r m3.Yut.Bt`)* were statistically significant positively associated with engagement rate, but not Instragram *(B=`r m3.Ins.B`, t=`r m3.Ins.t`, p  `r m3.Ins.p`, \(\beta\)=`r m3.Ins.Bt`)*.
+The main effect of negative emotional resonance emerged as statistically significant *(B=`r m3.neg.B`, t=`r m3.neg.t`, p  `r m3.neg.p`, \(\beta\)=`r m3.neg.Bt`)*, contrasting with the main effect of positive emotional resonance which did not manifest the same significance.
+*(B=`r m3.poz.B`, t=`r m3.poz.t`, p  `r m3.poz.p`, \(\beta\)=`r m3.poz.Bt`)*Both effects were observed to be moderated by the underlying social network.
+Furthermore, in comparison to the influence on Twitter, both Facebook and YouTube exhibited statistically significant positive associations with the engagement rate, a phenomenon not witnessed with Instagram.*(B=`r m3.Ins.B`, t=`r m3.Ins.t`, p  `r m3.Ins.p`, \(\beta\)=`r m3.Ins.Bt`)*.
 
@@
 
-Compared to Twitter posts, if the messages with positive emotional resonance were posted on Instagram or Youtube, the engagement rate increased statistically significant and the effect was most powerfull on Instagram than on Youtube.
-No interaction effect was observed on Facebook related on positive emotional resonance *(B=`r m3.PozFbk.B`, t=`r m3.PozFbk.t`, p  `r m3.PozFbk.p`, \(\beta\)=`r m3.PozFbk.Bt`)*
+Contrasting with Twitter posts, communications imbued with positive emotional resonance exhibited a statistically significant increase in engagement rate when disseminated on Instagram or YouTube, with the effect manifesting more potently on Instagram relative to YouTube.
+Notably, no interaction effect correlating with positive emotional resonance was observed on the Facebook platform.
+*(B=`r m3.PozFbk.B`, t=`r m3.PozFbk.t`, p  `r m3.PozFbk.p`, \(\beta\)=`r m3.PozFbk.Bt`)*
 
 # Discussion
-The current study embarked on an investigative journey to examine public engagement across a range of social media platforms utilized by the European Commission, laying specific emphasis on the impact of emotional resonance within disseminated content.
-The vital role of social media in communication strategies of public institutions has been widely recognized [@Smith2015], accentuating the necessity for an in-depth comprehension of the dynamics of engagement.
+The present research undertook a detailed exploration to examine public engagement across an array of social media platforms implemented by the European Commission, with particular attention dedicated to the influence of emotional resonance within the disseminated content.
+The paramount role of social media within the communication strategies of public institutions has been extensively acknowledged [@Smith2015], thus underscoring the exigency for a profound understanding of the intricacies of engagement dynamics.
 
@@
 
-Despite these findings, the study is not without limitations.
+Notwithstanding the above findings, it is essential to recognize the inherent limitations of this study.
 The scope of this research was confined to the European Commission's use of four primary social media platforms.
@@
 The ability to establish an emotional connection with the audience, made possible through well-conceived and executed posts, emerges as a powerful tool for amplifying engagement levels.
-Such engagement is not merely about expanding the reach or visibility of public institutions like the European Commission, but is a mechanism for fostering a dynamic and participatory relationship between these institutions and the citizens they serve.
+Such engagement transcends mere augmentation of reach or visibility of public institutions, such as the European Commission, and represents a conduit for cultivating a dynamic and interactive association between these institutions and the citizenry they serve.
 
@@
 
-To conclude, this study underscores the significance of emotional resonance and platform-specific norms in driving public engagement.
-It suggests that forming an emotional connection with the audience through posts could amplify engagement levels.
+In conclusion, this study accentuates the paramount importance of emotional resonance and platform-specific norms in stimulating public engagement.
+The findings infer that the formation of an emotional bond with the audience through meticulously constructed posts may serve to magnify the levels of engagement.
 By understanding these dynamics, public institutions like the European Commission can refine their social media strategies, enhance citizen engagement, and bolster the efficacy of their public communication.

### 2023-06-17 Article.Rmd
Final article

@@
 His combination of academic and professional experience has equipped them with the necessary skills and knowledge to excel in various fields of communication and administration.
-
     Cristian Opariuc-Dan (Orcid ID: https://orcid.org/0000-0003-4079-0142) is a lecturer at the Faculty of Law and Administrative Sciences at Ovidius University in Constanta.
@@
 With over 50 scientific articles published in specialized journals and as the author and co-author of 5 books in the field of statistics and data analysis, he has demonstrated his expertise in the academic field.
-
     Cristina-Dana Popescu (Orcid ID: https://orcid.org/0009-0009-5280-6608) is a Lecturer at the Faculty of Letters, the Faculty of Law and Administrative Sciences and at the Faculty of Mathematics and Informatics at Ovidius University in Constanta.
@@
 She also holds the qualification of Trainer, COR Code 242401, certified by SC Training & Teaching Center, București.With over 30 scientific articles published in specialized journals at national and international conferences, author of ISI and BDI articles, participant both in CNCSIS grant teams and in University Projects as Expert in the Study Programs Pillars and Expert in Educational Material Development and also author of 3 books and co-author of 1 book in the field of literature and various specialized languages, she has demonstrated her expertise in the academic field.
-
 abstract: |
@@
 output          :
-  pdf_document  : papaja::apa6_pdf
+  word_document : papaja::apa6_docx
   html_document :
     df_print    : paged
-  word_document : papaja::apa6_docx
+  pdf_document  : papaja::apa6_pdf
 ---
